---
title: "Do not disturb? Investigating the impact of disturbance on understorey seedling species in Langkawi Island's limestone rainforests"
author: 'Malaysia Statistics Group: Ruwan Joseph, Nicholas Ryan and Ricky Ng'
date: '13th November, 2017'
output:
  html_document:
    code_folding: hide
    df_print: paged
    fig_caption: yes
    fig_height: 3
    fig_width: 5
    highlight: tango
    number_section: yes
    theme: sandstone
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, fig.height = 3, fig.width = 5)

# Function to automatically install missing libraries and load all.
# Sourced from internet: 
instant_pkgs <- function(pkgs) {  
  pkgs_miss <- pkgs[which(!pkgs %in% installed.packages()[, 1])] 
  if (length(pkgs_miss) > 0) { 
    install.packages(pkgs_miss) 
  } 
  
  if (length(pkgs_miss) == 0) { 
    message("\n ...Packages were already installed!\n") 
  } 
  
  # install packages not already loaded: 
  pkgs_miss <- pkgs[which(!pkgs %in% installed.packages()[, 1])] 
  if (length(pkgs_miss) > 0) { 
    suppressPackageStartupMessages(install.packages(pkgs_miss)) 
  } 
  
  # load packages not already loaded: 
  attached <- search() 
  attached_pkgs <- attached[grepl("package", attached)] 
  need_to_attach <- pkgs[which(!pkgs %in% gsub("package:", "", attached_pkgs))] 
  
  if (length(need_to_attach) > 0) { 
    for (i in 1:length(need_to_attach)) 
      suppressPackageStartupMessages(require(need_to_attach[i], character.only = TRUE)) 
  } 
  
  if (length(need_to_attach) == 0) { 
    message("\n ...Packages were already loaded!\n") 
  } 
} 

# Define packages to load run instant_pkgs
packages_to_load <- c("readxl", "dplyr", "tidyr", "magrittr", "knitr",
                      "ggplot2", "ggthemes", "lubridate",
                      "lme4", "INLA", "stringr", "scales", "splines", "car", "grid")

instant_pkgs(packages_to_load)
```

```{r}
# Aesthetics for GGplot
bg_green <- rgb(223, 241, 204, maxColorValue = 255)
bg_table_pastel <- rgb(255, 242, 204, maxColorValue = 255)
colours.site = c("#d62121", "#30d621")
colours.splinefit = c("#b21515", "#21b623", colours.site[1], colours.site[2], "#d92121", "#33d621")

# Define backgroun_colour as bg_green for presentation
colours.background <- "white"

theme_project <- function() {
  theme_bw() +
  theme(legend.position = "top") +
  theme(legend.background = element_rect(colours.background),
        legend.box.background = element_rect(fill=colours.background, color=colours.background),
        legend.key = element_rect(fill=colours.background),
        plot.background = element_rect(colours.background, color=colours.background)) 
}

theme_table_pastel <- function() {
  theme_bw() +
  theme(legend.position = "top") +
  theme(legend.background = element_rect(bg_table_pastel),
        legend.box.background = element_rect(fill=bg_table_pastel, color=bg_table_pastel),
        legend.key = element_rect(fill=bg_table_pastel),
        plot.background = element_rect(bg_table_pastel, color=bg_table_pastel)) 
}

## Introduce multiplot function by Peter Haschke http://www.peterhaschke.com/r/2013/04/24/MultiPlot.html 
## This function is sourced from the internet. It is used to compare two plots of different datasets on a similar grid
multiplot <- function(..., plotlist = NULL, file, cols = 1, layout = NULL) {
  require(grid)

  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  if (is.null(layout)) {
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

  if (numPlots == 1) {
    print(plots[[1]])

  } else {
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    for (i in 1:numPlots) {
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

<!-- # Change Data Folder -->
```{r}
# Define the datafolder that contains all RDatasets. This will be an empty string when submitted
data_folder <- "C:\\Users\\Jacob\\Dropbox\\Semester 2 2017\\MXB344\\Project\\Data\\"
# data_folder <- ""
```

# Abstract
Limestone rainforests are well known for their high biodiversity, endemic species, and unique landscape. This investigation analysed understorey seedling functional traits of three dominant species in addition to abiotic factors in pristine and disturbed sites of a limestone rainforest on Langkawi Island, Malaysia. The research questions focused on determining how disturbance impacted diversity, specific leaf area, and temperature, and investigating surrogates for collecting resource expensive species richness data. 

Bayesian Generalised Linear Mixed Effect Models were used to investigate key relationships. Although variation was visually observed for transects and quadrats nested in transects (design), minimal variance was attributed to these random effects. According to the model, this suggests that future research in the rainforest may not require a transect design. 

The fixed effects showed disturbance resulted lower specific leaf area, driven by dominant species 1. The data however did not provide evidence that seedling cover, diversity or temperature were significantly different between sites. Instead, gap fraction threshold and dominant species were the main drivers of diversity and seedling cover. Temperature provided a mild indicator of species richness. Modelling provided strong evidence of positive or negative relationships, with uncertainty around the actual estimate effects. Further data is required to quantify more precise estimates and relationships, however this report provides important initial insights for future research.


# Background

_**Lankgawi Island's Limestone Rainforests**_

Natural rainforests are continually being destroyed by human infrastructure by the means of land clearing, agriculture, tourism, pollution and climate change. These negative influences are currently affecting the limestone rainforest on Langkawi Islands which is in conjunction to the forest clearing and logging already noticeable in other regions of Malaysia (McMorrow & Talip, 2001).


Limestone rainforests are well known for their high biodiversity and endemic species. This is due to the unique landscape and habitat which houses the species that have evolved to adapt to live on the limestone (Clements, Sodhi & Schilthuizen, 2006). Limestone rainforests are very unique and are a popular research location; signifying the importance of this investigation and analysis. This is also the first time data and analysis have been performed on this area. 

_**Understorey Seedling Species**_

Due to the scope of this project it was decided to focus on the understorey of the rainforest. This was for multiple logistic reasons and findings in past literature. This did not limit the study as the understorey of rainforests have been shown to be incredibly important with particular variables being good predictors. Understorey's have continuously been used to investigate disturbed forests. One example looked at different forest understorey's in the Philippines, a main finding being higher species richness in the disturbed (Wills et al., 2016). 

Studies also explored disturbance and the difficulties of restoration. They showed that functional traits act a filter, in a sense, for the types of plant species able to inhabit particular ecosystems. These can include an array of features that are only suitable for specific species. Species without specific functional traits cannot inhabit certain communities (Funk et al., 2008)

_**Dominant Species**_

We also found past research that introduced the concept of dominant plant species influencing ecosystems. Meaning their functional traits may contribute to their survival in disturbed ecosystems, being able to bypass the filters posed by disturbance (Wangchuk et al., 2014). This then leads to the backbone of this study that the understorey is the future of the rainforest signifying its importance for this study. 

_**Target Resolutions**_

From our study and what we have learned from our research we aimed to quantify the factors of disturbance and relate it all back to the ecological effects on the ecosystems. Our study will then lead the next two years of research to extend what we completed and add more research to the Limestone Forests on Langkawi Island.

## Research Questions
The three main research questions are:

  1. Is the cover, Shannon's diversity index and specific leaf area of the three dominant species in the forest (either individually or together) different between pristine and disturbed areas of the limestone forest? If so, then how do these differ between the two areas?
  2. Is the temperature and humidity different between pristine and disturbed areas of the limestone forest?
  3. Can species richness be predicted based on other data which are much cheaper (in terms of time and effort) to collect?

At a high level, abiotic indicators are investigated to quantify the disturbance conditions of the rainforest. Where as biotic variables are investigated to evaluate the impact of this disturbance on the ecosystem. Each question will be explain in further detail to identify the ecological meaning.

### Dominant Species Seedling Cover
In previous studies, the plant cover of a specific species is an indicator to the nutrients stored in the soil; this is because the cover contributes to the governance of soil erosion (Pohl, Graf, Buttler, & Rixen, 2012). In addition, it was proven in other forest types that the combined contribution of seedling cover and high species richness is significantly more effective at governing soil erosion (Pohl et al., 2012).  Disturbance implies for the presence of species that are more resilient to the lack of necessary nutrients, and thereby affecting the level of seedling cover in an area (Funk,2008). For example, a fire can burn up to the entire understorey; which promotes the growth of pioneer species that disperse and grow quicker in disturbed forests (Fourrier et al., 2015). These species typically need high photosynthetic rate, growth capacity, and nutrient storage to recover from recent disturbances (Manninen, Stark, Kytaviita, Lampinen, & Tolvanen, 2009). The different types of disturbances can affect how the plants grow, and therefore may contribute to the changes in seedling cover.



### Dominant Species Shannon's Index of Diversity
Shannon's Diversity Index is calculated using the abundance multiple by the natural logarithm of the abundance. This index accounts for the abundance in addition to the evenness of all other species. It is also suggested that ecosystem function decline can be alleviated with dominant species becoming prevalent in the ecosystem (Grime, 1998). 

Species diversity is a standard variable calculated in ecological studies. Previous studies have looked at the diversity of a particular trees in Malaysia and found adverse effects of diversity on the overall biodiversity of the forest (Addo-Fordjour, Rahmad & Shahrul, 2012). This study also was on disturbed forests due to tourism, which is a major industry in Malaysia and Langkawi Island. 

Other studies suggested that increased disturbance leads to high diversities due to advantageous/fast growing species (Nguyen et al., 2012). One particular study also focused on only dominant species and found their diversity was a good indicator of disturbance (Stevens et al., 2015). This was reiterated in an understorey study on ecosystem functions in forests of varying soil types, elevation and weather conditions (Duguid et al., 2013). 

All of these studies show that the diversity of dominant species change in response to disturbance, and Shannon's Diversity Index is a useful tool. 

### Dominant Species Specific Leaf Area

_**Specific Leaf Area**_

The purpose of investigating specific leaf area, referred to as SLA in this report, is the insight is provides into a plants strategy in the ecosystem. Plants are in constant competition for resources within their community. One core resource required is light. This presents one of the most competitive strategies employed by a plant: how they invest growth into their leaves, the apparatus used to capture light. A larger leaf will capture more light, and enable faster growth. However, with a limited amount of energy available, the plant must sacrifice the thickness of their leaves. This makes the plant more susceptible to damage from herbivores.

This presents a trade-off between the growth and defence mechanisms of the plant. SLA is a measure of this trade-off, calculated as the one-sided leaf area divided by the dry mass. SLA is used to relatively compare different species within the same community, categorising plants as resource acquisition or resource conservation. A relatively high SLA can suggest the plant has a need to compete more aggressively for light that other species within the same community (Quested et al., 2007).

_**Investigation of Weighted and Aggregated SLA**_

To provide a thorough comparison of the SLA between species and between disturbance, the SLA is weighted by each plants contribution to the community. This is calculated as the SLA of each leaf, weighted by the amount of area coverage the plant has in its community. This weighting takes into account how established a plant is in the community, and provides an insight to how this dominance affects a plant's investment strategy. This weighted measure is used to quantify the difference between species. To measure the difference due to disturbance, each species is aggregated to the community level. From Grime 2004, we know that dominant species have a large influence on the ecosystem, so this aggregation determines the growth strategy of the community (Pakeman et al., 2008).

### Temperature
Disturbed areas of a rainforest exhibit trait that change the environmental conditions of the ecosystem. One outcome of this disturbance is generally an increase in temperature, as a result from the exposure from the canopy cover (De Lima et al., 2013). 

### Species Richness
Species richness in ecology is discussed to illustrate the quantity of species in an area, but does not account for diversity. In 1973, the classic humped-back model(HBM) was theorised, stating that the productivity of an ecosystem peaks when species richness also peaks (Fraser et al., 2015). Although there is conflict between academic resources concerning the validity of this model, it is a phenomena still investigated in ecology (Ashouri, Jalili, Danehkar, Chahouki, & Hamzeh'ee, 2016). Studies have indicated that disturbances, evolutionary history, temperature, and dispersal limitations are also likely to contribute to species richness (Ashouri et al., 2016).  However, the variable of temperature is complicated as its implication on species richness depends on the competitiveness in the environment (Hillebrand, Burgmer, & Biermann,2012). Therefore, other variables derived from the environment may possibly predict species richness. 










# Experimental Design



```{r, child = '001_experimental_design.Rmd'}
```

# Data
All raw data collected throughout the experiment was compiled into a single excel workbook. This data was cleaned and manipulated into five modelling datasets, for each research question. All numeric predictor variables are scaled to the standard normal distribution, to prevent numerical errors in the model development and enable a fair comparison between estimates.

```{r, child = '010_data_preparation.Rmd'}
```

Prior to analysis, the data quality was evaluated. Major outcomes were that humidity data remained at a constant 100%, outliers were detected for temperature readings and the canopy analyser data was unbalanced. The research focus on relative humidity was not continued further, as not model could be derived. The temperature outliers were removed, and the imputing method was used to enable leaf area index and gap fraction threshold data to be analysed. Further details are included in Appendix 1: Data Quality.









# Analysis Overview
The models used throughout this report are generalised linear mixed effects models. This section will outline how and why these models are required, and will provide an overview of the model development process.

_**Mixed Effects**_

Mixed effects models enable the variation of the response variable to be explained by fixed and random effects. Fixed effects represent the predictor variables that are of direct interest, such as disturbance or dominant species id. Random effects represent variables that are known to cause variation in the response variable, but are not of direct interest.
  
The fixed effects include all abiotic and biotic variables that are collected throughout the experiment. The final model will represent the most predictive subset of these variables. The random effects of each model include variation between transects, and variation between quadrats nested in transects. This structure is necessary due to the experimental design, and will remain constant for every model (i.e. not form part of the model selection).

_**Generalised Linear Mixed Effects**_

The choice between a linear mixed effects model (LMM) and generalised linear mixed effects model (GLMM) depends on the domain of the response variable. GLM's transform the predictors of the linear model from the real scale into the correct domain through a link function. For example, Species Richness can only be a positive integer value. Thus, a Poisson GLM can be used with a log-link function to model the average species richness.

_**Bayesian Model**_

The Bayesian paradigm is utilised for it's ability to handle a mixed effects structure in GLMM's. The mixed effects structure requires the likelihood conditional on the random effects. The frequentist paradigm is limited as it requires the difficult integration of this conditional probability, with various approximation methods used. However, the Bayesian paradigm uses this probability directly and more efficiently. The modelling method used throughout this report is Integrated Nested Laplace Approximation (INLA). Essentially, INLA matches the posterior distribution of each parameter based on the mode and spread of the data.

The Bayesian model estimates a distribution for each parameter in the model. These distributions are interpreted using 95% Credible Intervals, which evaluates the 2.5% and 97.5% quantiles of the distribution. If this interval does not include zero, then the collected data provides evidence that the parameter has a positive or negative effect. The uncertainty around this parameter is evaluated as range between these quantile estimates. As such, the predictor variable's effect on the response variable will be reported with a lower and upper bound estimate.

_**Process Overview**_

This section demonstrates the model development process. The data is explored through meaningful graphs that identify visual patterns within the data. This information guides the model development, which aims to quantify the relationships between the predictor and response variable. 

  * Model/variable selection is evaluated on the maximum Marginal log-Likelihood and Credible Intervals that do not contain zero. 
    * Additional credible intervals are shown that demonstrate the real effect of parameters with interactions.
  * Model fit is evaluated on residual plots and whether the CPO PIT values are approximately uniformly/normally distributed.

The following subsections are segmented into an exploratory analysis and model development of each research question's response variables. 

# Temperature
## Exploratory Analysis
```{r, child = '020_exploratory_temperature.Rmd'}
```

## Model Development
```{r, child = '021_model_temperature.Rmd'}
```

## Model Outcomes
High amounts of serial correlation were found in the dataset. After the random effects structure accounted for some of this variation, there was no significant difference between sites.













# Seedling Cover
## Exploratory Analysis
```{r, child = '030_exploratory_cover.Rmd'}
```

## Model Development
```{r, child = '031_model_cover.Rmd'}
```

## Model Outcomes
The variables remaining through the model fit procedure were the abundance of dominant species and their species identification; disturbance did not appear likely to be a significant variable to the seedling cover of dominant species. However, the results of the regression demonstrated that each species contributes differently to the seedling cover; the presence of dominant species 2 implied that there was relatively higher seedling cover compared to dominant species 1 and 3. Furthermore, the regression showed that the abundance of dominant species has a positive effect on the seedling cover. 












# Shannon's Index of Diversity
## Exploratory Analysis
```{r, child = '040_exploratory_shannons.Rmd'}
```

## Model Development
```{r, child = '041_model_shannons.Rmd'}
```


## Model Outcomes
There was no difference in Shannon's Index between sites, but there was higher variation in the disturbed transects. This follows a suggestion that arose that disturbed areas are more adaptive to the conditions. We also saw relationships between the overall seedling cover, total dominant leaf dry weight, average quadrat Gap Fraction Threshold and the interaction between site and overall seedling cover. 

GFT, overall seedling cover and total overall dominant dry leaf weight increased Shannon's Index. The interaction between site and seedling cover, after adding together overall seedling cover and the interaction, the effect is no longer a predictive variable.















# Specific Leaf Area
As SLA can only equal values between zero and infinity, the log of SLA will be modelled. 

## Aggregated
The following subsections investigate key relationships that explain the community aggregated SLA, which includes 30 observations. 

### Exploratory Analysis
```{r, child = '050_exploratory_sla_cagg.Rmd'}

```

### Model Development
```{r, child = '051_model_sla_cagg.Rmd'}

```

## Individual Species
The following subsections investigate key relationships that explain the variation of community weighted SLA.
  

### Exploratory Analysis
```{r, child = '052_exploratory_sla_cweight.Rmd'}

```

### Model Development
```{r, child = '053_model_sla_cweight.Rmd'}

```


## Model Outcomes
Overall, the model estimates a distinct difference between disturbed and undisturbed forest areas. Upon investigating each individual species, this difference between sites can be attributed to dominant species 1. Both dominant species 2 and 3 had less weighted SLA than species 1, and the parameter estimates showed no major differences between rainforest sites.














# Species Richness
## Exploratory Analysis
```{r, child = '060_exploratory_richness.Rmd'}
```

## Model Development
```{r, child = '061_model_richness.Rmd'}
```


## Model Outcomes
Through a model fit procedure, the only variable that was likely to be significant to the model was the maximum temperature in the given area. From the regression, it appears to have a negative relationship with species richness; as the maximum temperature increases, the species richness decreases. 






# Discussion
## Ecological Meaning of Model Outcomes

_**Temperature**_

No significant difference was modelling between disturbed and undisturbed areas of the rainforest. This is a result of the lack of data available, and the complexity of modelling serial correlation. However, a slight difference can be visually observed, suggesting that the disturbed areas have certain characteristics that increase temperature.

_**Seedling Cover**_

From the analysis, it is demonstrated that the disturbance does not impact the seedling cover in an area. However, it was found that the individual dominant species had a varying impact on the seedling cover; with species 2 contributing the most. In this way, it indicates that these dominant species, particularly species 2, are important to the seedling cover. With more seedling cover, there is soil erosion protection, and therefore this analysis indicates the importance of these species. Furthermore, the analysis indicated the impact of abundance to the seedling cover. While this may appear intuitive, it is important to reiterate that since the seedling cover protects the nutrients for neighbouring plants, it implies that abundance is also important for the protection of these nutrients. 

_**Shannons Index of Diversity**_

In terms of ecological meaning, the model investigating Shannon's index tell us that diversity does not appear to change between disturbed and pristine sites. Other factors affected diversity. It increased with higher cover of all seedlings, possibly explained by the advantageous species in disturbed ecosystems utilising the expose ground and nutrients. Higher GFT tells us that diversity increased with less canopy cover which also may explain the higher dominant leaf dry weight as larger leaves utilise sunlight better. 

_**Specific leaf Area**_

From the community aggregated and community weighted SLA models, we can infer that dominant species 1 is a resource acquisition specialist in pristine rainforests conditions, after accounting for the seedling coverage. Species 1 exhibited a distinctly different investment strategy when disturbance factors were not present, suggesting that species 1 experiences more competition in pristine rainforest conditions. At an aggregated level, the pristine rainforest areas were found to have a estimated larger SLA. However, majority of this difference is attributed to the growth strategies of species 1.

_**Species Richness**_

From the analysis, it is demonstrated that the disturbance does not impact the seedling cover in an area. However, it was found that the individual dominant species had a varying impact on the seedling cover; with species 2 contributing the most. In this way, it indicates that these dominant species, particularly species 2, are important to the seedling cover. With more seedling cover, there is soil erosion protection, and therefore this analysis indicates the importance of these species. Furthermore, the analysis indicated the impact of abundance to the seedling cover. While this may appear intuitive, it is important to reiterate that since the seedling cover protects the nutrients for neighbouring plants, it implies that abundance is also important for the protection of these nutrients. 






# Conclusion and Recommendations
The findings of this project reveals information that can be used to protect the limestone forests. The implications to the future of limestone forests are derived in this study of seedling species in accordance to the plant cover, species richness, SLA, diversity, and temperature. 

While the analysis indicated that the disturbances of the limestone rainforests does not contribute to the seedling cover, it was found that each dominant species had a significant role in the growth in seedling cover. Recall that the seedling cover is also the governance of soil erosion protection. Furthermore the abundance of the three dominant species has a significant positive effect on the plant cover. Therefore, from the analysis of the seedling cover, it is to be deduced that there is importance in protecting the three dominant species to ensure seedling cover. 

In examining the effects of disturbance on the temperature, it was found that disturbance did not significantly suggest a higher temperature. 

While the Shannon's Index of Diversity is not dependent on the disturbance, it appears to be dependent on other variables such as higher seedling cover, GFT, and leaf dry weight. These variables all imply for a higher diversity of dominant species.

The specific leaf area was found to differ between disturbances as well as affect be affected differently according to the specific leaf. Species 1 was more likely to have a larger weighted SLA in pristine forest. 

Finally, it was found that higher temperatures implied lower species richness. That is, species richness has a negative relationship with the maximum temperature. 

The implications of our findings show how disturbance affects the limestone rainforests in Langkawi Island and the relationships with several important attributes. The understanding of the dominant seedling species can predict the future of the forest, and therefore the negative impacts of future seedling species. We have also highlighted key relationships that can be used to determine similar relationship in limestone rainforests. These relationships can also be built upon for future research, while addressing the brief limitations, attached in Appendix 2.


# Appendix
## Appendix 1: Data Quality
```{r, child = '011_data_quality.Rmd'}
```

## Appendix 2: Limitations
The first limitation occurred for the leaf sample measurements, due the low sensitivity of the weighing scales. This was overcome by measuring the total weight of all leaf samples, per species per quadrat, and calculating the mean. This provides misleading results for the small or large leaves of the sample, which deviate significantly from the mean weight. We advise bring appropriate scales or obtaining/borrowing them from the local university or labs. 

The main limitation was due to the equipment available for the experiment overseas. No oven was available for drying leaves or filter paper, which resulted in the moisture content being an uncontrolled variable. This affects the dry leaf mass and filter paper weight measurements. Again, it is recommended to arrange borrowing equipment from local university or technical labs. 

Another limitation was a result of the limited time available to collect data such as temperature readings and soil decomposition. This prevented a thorough analysis of the variation in temperature at the rainforest. This also prevented the filter paper to adequately capture any difference in decomposition rates from the rainforest. One solution is to ensure that on the first day/on arrival the data loggers are placed where they need to go. 



# References
  1. Addo-Fordjour, P., Rahmad, Z., & Shahrul, A. (2012). Effects of human disturbance on liana community diversity and structure in a tropical rainforest, Malaysia: implication for conservation. Journal Of Plant Ecology, 5(4), 391-399. http://dx.doi.org/10.1093/jpe/rts012
  2. Ashouri, P., Jalili, A., Danehkar, A., Chahouki, M. A. Z., & Hamzeh'ee, B. (2016). Is there any support for the humped-back model in some steppe and semi steppe regions of iran? Acta Oecologica, 73, 61-70. doi:10.1016/j.actao.2016.03.002
  3. De Lima, Nádia Gilma Beserra, Galvani, E., Falcão, R. M., & Cunha-Lignon, M. (2013). Air temperature and canopy cover of impacted and conserved mangrove ecosystems: A study of a subtropical estuary in brazil. Journal of Coastal Research, 2(65), 1152-1157. doi:10.2112/SI65-195
  4. Clements, R., Sodhi, N., Schilthuizen, M., & Ng, P. (2006). Limestone Karsts of Southeast Asia: Imperiled Arks of Biodiversity. Bioscience, 56(9), 733-742. http://dx.doi.org/10.1641/0006-3568(2006)56[733:lkosai]2.0.co;2
  5. Duguid, M., Frey, B., Ellum, D., Kelty, M., & Ashton, M. (2013). The influence of ground disturbance and gap position on understory plant diversity in upland forests of southern New England. Forest Ecology And Management, 303, 148-159. http://dx.doi.org/10.1016/j.foreco.2013.04.018
  6. Fraser, L., Pither, J., Jentsch, A., Sternberg, M., Zobel, M., Askarizadeh, D., . . . Zupo, T. (2015). Worldwide evidence of a unimodal relationship between productivity and plant species richness. Science, 349(6245), 302-305. doi:10.1126/science.aab3916
  7. Funk, J., Cleland, E., Suding, K., & Zavaleta, E. (2008). Restoration through reassembly: plant traits and invasion resistance. Trends In Ecology & Evolution, 23(12), 695-703. http://dx.doi.org/10.1016/j.tree.2008.07.013
  8. Grime, J. (1998). Benefits of plant diversity to ecosystems: immediate, filter and founder effects. Journal Of Ecology, 86(6), 902-910. http://dx.doi.org/10.1046/j.1365-2745.1998.00306.x
  9. Hillebrand, H., Burgmer, T., & Biermann, E. (2012). Running to stand still: Temperature effects on species richness, species turnover, and functional community dynamics. Marine Biology, 159(11), 2415-2422. doi:10.1007/s00227-011-1827-z
Cancel
  10. McMorrow, J., & Talip, M. (2001). Decline of forest area in Sabah, Malaysia: Relationship to state policies, land code and land capability. Global Environmental Change, 11(3), 217-230. http://dx.doi.org/10.1016/s0959-3780(00)00059-5
  11. Nguyen, H., Herbohn, J., Firn, J., & Lamb, D. (2012). Biodiversity-productivity relationships in small-scale mixed-species plantations using native species in Leyte province, Philippines. Forest Ecology And Management, 274, 81-90. http://dx.doi.org/10.1016/j.foreco.2012.02.022
  12. Pakeman, R., Garnier, E., Lavorel, S., Ansquer, P., Castro, H., Cruz, P., . . . Vile, D. (2008). Impact of Abundance Weighting on the Response of Seed Traits to Climate and Land Use. Journal of Ecology, 96(2), 355-366. Retrieved from http://www.jstor.org.ezp01.library.qut.edu.au/stable/20143472 
  13.Quested, H., Eriksson, O., Fortunel, C., & Garnier, E. (2007). Plant Traits Relate to Whole-Community Litter Quality and Decomposition following Land Use Change. Functional Ecology,21(6), 1016-1026. Retrieved from http://www.jstor.org.ezp01.library.qut.edu.au/stable/20142742 
  14. Stevens, J., Safford, H., Harrison, S., & Latimer, A. (2015). Forest disturbance accelerates thermophilization of understory plant communities. Journal Of Ecology, 103(5), 1253-1263. http://dx.doi.org/10.1111/1365-2745.12426
  15. Wangchuk, K., Darabant, A., Rai, P., Wurzinger, M., Zollitsch, W., & Gratzer, G. (2014). Species richness, diversity and density of understory vegetation along disturbance gradients in the Himalayan conifer forest. Journal Of Mountain Science, 11(5), 1182-1191. http://dx.doi.org/10.1007/s11629-013-2942-8
  16. Wills, J., Herbohn, J., Moreno, M., Avela, M., & Firn, J. (2016). Next-generation tropical forests: reforestation type affects recruitment of species and functional diversity in a human-dominated landscape. Journal Of Applied Ecology, 54(3), 772-783. http://dx.doi.org/10.1111/1365-2664.12770


