---
title: "model_development"
output: html_document
---

Before building the modelling datasets, quality of the collected data is assessed.

```{r}
load(paste0(data_folder, "hobo_nofilter2.RData"))




# Plot the graphs
# Create 6 hour intervals for time series graphs
start <- as.POSIXct(strptime("2017-09-25 04:00:00", "%Y-%m-%d %H:%M:%S"))
interval <- 60*6
end <- start + as.difftime(4, units="days")
labels = seq(from=start, by=interval*60, to=end)

# Create just the time intervals instead, since shading is used for days
start2 <- as.POSIXct(strptime("2017-09-25 18:00:00", "%Y-%m-%d %H:%M:%S"))
end2 <- start + as.difftime(5, units="days")
labels2 = seq(from=start2, by=interval*60, to=end2)
time_labels = format(labels2, format = "%H:%M:%S")

labels = labels[2:17]
time_labels <- substr(time_labels[2:17], 1, 5)

# Show filter point for late hobos
min_new_time <- as.POSIXct(strftime("2017-09-28 03:00:00", "%Y-%m-%d %H:%M:%S"))

latehobos <- data.frame(ytemp = c(25.5, 28),
                        xdatetime = c(min_new_time, min_new_time)) %>%
  tbl_df

hobo_days_humid <- data.frame(startday = c(as.POSIXct(strftime("2017-09-25 22:00:01", "%Y-%m-%d %H:%M:%S")),
                                     as.POSIXct(strftime("2017-09-26 00:00:00", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-27 00:00:00", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-28 00:00:00", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins")),
                        endday =   c(as.POSIXct(strftime("2017-09-25 23:59:59", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-26 23:59:59", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-27 23:59:59", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-29 01:00:00", "%Y-%m-%d %H:%M:%S")))) %>%
                        mutate(day = c("Monday", "Tuesday", "Wednesday", "Thursday"),
                               day = factor(day,
                                            levels = c("Monday", "Tuesday", "Wednesday", "Thursday"),
                                            ordered = TRUE)) %>% 
  tbl_df()
```

_Relative Humidity_

The data collected from the HOBO devices produced humidity data that reaches a constant 100%. As such, the research question involving relative humidity is not investigated further, as the collected data presents no difference between disturbed and undisturbed areas of the rainforest. This is observed from the figure below.

```{r}
ggplot() +
  theme_project() +
  scale_x_datetime(breaks = labels
                   ,labels = time_labels
                   ) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1)) +
  geom_rect(aes(xmin=startday, xmax=endday, ymin = 65, ymax = 100, fill = day),
            data = hobo_days_humid, alpha = 0.4)   +
  scale_fill_tableau(name = "Day")+
  geom_point(aes(x=date_time, y=rel_humid),
             data = hobo_nofilter2.df, size=1) +
  # scale_colour_continuous(low = colours.site[1], high = colours.site[2], name = "Elevation")  +
  ggtitle("Humidity over Time") +
  xlab("Time of Day") +
  ylab("Relative Humidity (%)") +
  theme(legend.background = element_rect(bg_green),
        legend.box.background = element_rect(fill=bg_green, color=bg_green),
        legend.key = element_rect(fill=bg_green),
        plot.background = element_rect(bg_green, color=bg_green)) +
  geom_line(aes(x=xdatetime, y=ytemp),
            data = latehobos) +
  scale_y_continuous(lim = c(65, 100))

```

_Temperature_

In the temperature data, distinct outliers are observed at the initial and final readings. These correspond to operator handling errors during the experiment set up. These are removed to ensure a reliable comparison between temperature readings. The outliers are observed in the figure below.

```{r}
yaxis_min <- min(hobo_nofilter2.df$temp)
yaxis_max <- max(hobo_nofilter2.df$temp)

ggplot() +
  theme_project() +
  scale_x_datetime(breaks = labels
                   ,labels = time_labels
                   ) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1)) +
  geom_rect(aes(xmin=startday, xmax=endday, ymin = yaxis_min, ymax = yaxis_max, fill = day),
            data = hobo_days_humid, alpha = 0.4)   +
  scale_fill_tableau(name = "Day")+
  geom_point(aes(x=date_time, y=temp),
             data = hobo_nofilter2.df, size=1) +
  # scale_colour_continuous(low = colours.site[1], high = colours.site[2], name = "Elevation")  +
  scale_colour_manual(values = colours.site) +
  ggtitle("Temperature over Time") +
  xlab("Time of Day") +
  ylab("Temperature") +
  theme(legend.background = element_rect(bg_green),
        legend.box.background = element_rect(fill=bg_green, color=bg_green),
        legend.key = element_rect(fill=bg_green),
        plot.background = element_rect(bg_green, color=bg_green)) +
  # geom_line(aes(x=xdatetime, y=ytemp),
  #           data = latehobos) +
  scale_y_continuous(lim = c(yaxis_min, yaxis_max))

```


_Canopy Analyser: LAI and GFT_
The canopy analyser was not able to collect data on the remaining two disturbed transects. To account for this imbalance, the imputing method was used with the average value from the first disturbed transect. The imbalance for these variables can be visually observed in the figure below. Three transect replicates of Pristine rainforest areas are recorded, compared to only one replicate of the Disturbed rainforest area.

```{r}
# LAI
lai1 <- ggplot(aes(x=paste0(site, ":", transect), y=lai, col = site),
       data = abiotic_canopycover.df) + 
  # geom_point() +
  geom_boxplot() +
  ggtitle("Leaf Area Index") +
  theme_project()+
  scale_colour_manual(values = colours.site) +
  xlab("Site:Transect") +
  ylab("Imbalance of LAI") +
  theme(legend.background = element_rect(bg_green),
        legend.box.background = element_rect(fill=bg_green, color=bg_green),
        legend.key = element_rect(fill=bg_green),
        plot.background = element_rect(bg_green, color=bg_green))

gft1 <- ggplot(aes(x=paste0(site, ":", transect), y=gft, col = site),
       data = abiotic_canopycover.df) + 
  # geom_point() +
  geom_boxplot() +
  ggtitle("Imbalance of GFT") +
  theme_project()+
  scale_colour_manual(values = colours.site) +
  xlab("Site:Transet") +
  ylab("Gap Fraction Threshold") +
  theme(legend.background = element_rect(bg_green),
        legend.box.background = element_rect(fill=bg_green, color=bg_green),
        legend.key = element_rect(fill=bg_green),
        plot.background = element_rect(bg_green, color=bg_green))

multiplot(lai1, gft1,
          layout = matrix(c(1,2), nrow=1))
```

_Elevation_

Elevation was a confounding variable as the experimental design placed all disturbed transects at a lower elevation to pristine transects. As the main interest of this research was a comparison between disturbed and pristine areas, the elevation variable is excluded from further analysis. This confounding is observed in the figure below.

```{r}
load(paste0(data_folder, "abiotic_elevation.RData"))

abiotic_elevation.df %>%
  select(elevation, site, transect) %>%
  distinct() %>%
  ggplot(aes(x=paste0(site, ":", transect), y=elevation, col = site)) +
  geom_point(size=2.27) +
  geom_boxplot() +
  xlab("Site") +
  ylab("Elevation (m)") +
  theme_project() +
  scale_colour_manual(values = colours.site) +
  theme(legend.background = element_rect(bg_green),
        legend.box.background = element_rect(fill=bg_green, color=bg_green),
        legend.key = element_rect(fill=bg_green),
        plot.background = element_rect(bg_green, color=bg_green)) +
  ggtitle("Elevation vs Sites and Transects")

```