---
title: "model_development"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_datasets_exploratory_analysis}
# This code should be removed when entire process is productionised
dropbox <- "C:\\Users\\Jacob\\Dropbox\\Semester 2 2017\\MXB344\\Project\\Data\\"

load(paste0(dropbox, "domseedlingcover_rq1.RData"))
load(paste0(dropbox, "domshannons_rq1.RData"))
load(paste0(dropbox, "domsla_rq1.RData"))
load(paste0(dropbox, "species_richness_rq3.RData"))
load(paste0(dropbox, "hobo_rq2.RData"))
```

This section provides an insight to the trends in the collected data. This analysis will be focused on individual research questions. This will provide interpretability when developing the statistical model.

## Research Question 1: Dominant Species Seedling Cover
```{r}
domseedlingcover_rq1.df

```

### Site vs Dominant Seedling Cover
In the figure below, we observe:

  * a slighty larger variance for domiannt species 1 and 2 in pristine sites.
  * higher IQR and medians for dominant species 1 and 2 in pristine sites
  * domiant species 3 is less evident in pristine sites
  * the coverage dominant species 4 is insignificant in comparison to the other 3
  
```{r}
domseedlingcover_rq1.df %>%
  select(dom_species_id, site, dom_seedling_cover, transect, quadrat) %>%
  distinct() %>%
  filter(!is.na(dom_species_id)) %>%
  ggplot(aes(x = factor(dom_species_id), y = dom_seedling_cover, col = site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_tableau() +
  ggtitle("Dominant Seedling Cover vs Site")

```




## Research Question 1: Dominant Species Shannons index of Diversity
```{r}
domshannons_rq1.df %>% str()
```

```{r}
domshannons_rq1.df %>%
  ggplot(aes(x = paste0(site,transect), y = dom_shannon)) +
  geom_point() +
  theme_project() +
  scale_colour_tableau() +
  ggtitle("Dominant Shannons Index vs Site")


```


  * overall
  * differ between individuals
  * Rao Tao (quadratic entropy)
  * Shannon
    * Diversty contrained by dominant
    * Try and group by a specific species? Use just P*log(p)
  * Just look at a the 'shannons for each species (3), for each site (so 6 in total, transect could make it 18.. but cant model it)
  



## Research Question 1: Dominant Species Specific Leaf Area
```{r}
dataq3 <- domsla_rq1.df
```

  * leaf area - photosynthetic aparatus of the plant
  * amount of investment of dry matter (plant investment into growth defence trade off) -> Most dominant species most compettitive, higher specific leaf area


```{r}
dataq3 %>%
  ggplot(aes(x=factor(dom_species_id), y = dom_sla, col=site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_tableau() +
  ggtitle("SLA vs Site and Dominant Species ID")

```


### Species Diversity: Abundance vs SLA
```{r}
dataq3 %>%
  ggplot(aes(x = dom_sla, y = dom_abundance, col = factor(dom_species_id))) +
  geom_density()


```



## Research Question 2: Hobo Time Series
```{r}
library(scales)

# Create 6 hour intervals for time series graphs
start <- as.POSIXct(strptime("2017-09-25 04:00:00", "%Y-%m-%d %H:%M:%S"))
interval <- 60*6
end <- start + as.difftime(4, units="days")
labels = seq(from=start, by=interval*60, to=end)

# Filter the data between useable dates
datarq2 <- hobo_rq2.df # Ten Hour Lag..


# Get shading for different days
hobo_days <- data.frame(startday = c(as.POSIXct(strftime("2017-09-26 3:00:01", "%Y-%m-%d %H:%M:%S")),
                                     as.POSIXct(strftime("2017-09-26 00:00:00", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-27 00:00:00", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-28 00:00:00", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins")),
                        endday =   c(as.POSIXct(strftime("2017-09-25 23:59:59", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-26 23:59:59", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-27 23:59:59", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-28 22:00:00", "%Y-%m-%d %H:%M:%S")))) %>%
                        mutate(day = c("Monday", "Tuesday", "Wednesday", "Thursday"),
                               day = factor(day,
                                            levels = c("Monday", "Tuesday", "Wednesday", "Thursday"),
                                            ordered = TRUE)) %>% 
  tbl_df()

# Plot the graphs
ggplot() +
  theme_project() +
  scale_x_datetime(breaks = labels
                   # labels = labels
                   # limits = c(as.POSIXct(strptime("2017-09-25 18:00:00",
                   # "%Y-%m-%d %H:%M:%S")) + as.difftime(10, units="hours"),
                              # as.POSIXct(strptime("2017-09-28 12:00:00",
                   # "%Y-%m-%d %H:%M:%S")) + as.difftime(10, units="hours"))
                   ) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1)) +
  geom_rect(aes(xmin=startday, xmax=endday, ymin = 25.8, ymax = 28, fill = day),
            data = hobo_days, alpha = 0.4)   +
  scale_fill_tableau(name = "Day")+
  # geom_line(aes(x=date_time, y=temp, col=hobo_id),
             # data = datarq2, size=1) +
  # scale_colour_pander(name = "Hobo ID")+
  geom_line(aes(x=date_time, y=temp, col=site),
             data = datarq2, size=1) +
  scale_colour_pander(name = "Site") +
  ggtitle("Temperature over Time") +
  xlab("Time of Day") +
  ylab("Temperature (Degrees Celsius)")

```











# Data
```{r}
# Use the choose files function to get the location of the datasets on your computer
# choose.files()

# Should get an output like:
# "C:\\Users\\Jacob\Project\\Data\\biotic_leaftraits.RData"

# Copy the folder spot below, and copy the """".RData file into the load function below

location <- "C:\\Users\\Jacob\\Dropbox\\Semester 2 2017\\MXB344\\Project\\Data\\"

# Load the datasets
load(paste0(location, "biotic_leaftraits.RData"))
load(paste0(location, "abiotic_filterpaper.RData"))
load(paste0(location, "abiotic_canopycover.RData"))
load(paste0(location, "abiotic_penetrometer.RData"))

```

## Abiotic
```{r}
# Decopmosition
ggplot(aes(x=site, y=decomposition),
       data = abiotic_filterpaper.df) + 
  geom_boxplot() +
  ggtitle("Abiotic Comparison") 



# LAI
ggplot(aes(x=site, y=lai, col = site),
       data = abiotic_canopycover.df) + 
  geom_boxplot() +
  ggtitle("Abiotic Comparison") 

# Gap fResction THreshold
ggplot(aes(x=site, y=gft, col = site),
       data = abiotic_canopycover.df) + 
  geom_boxplot() +
  ggtitle("Abiotic Comparison") 

# Compaction
ggplot(aes(x=site, y=compaction, col = site),
       data = abiotic_penetrometer.df) + 
  geom_boxplot() +
  ggtitle("Abiotic Comparison") 

```

## Leaf Traits
```{r}
count_data <- biotic_leaftraits.df %>%
  filter(species_presence == 1) %>%
  group_by(site, apex_shape) %>% # CHANGE LEAF TRAIT
  summarise(number_observations = n())

# CHANGE THE X VARIABLE LEAF TRAIT TO THE ONE ABOVE
ggplot(aes(x=apex_shape, y=number_observations, fill = site),
       data = count_data) + 
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  ggtitle("Leaf Trait Comparison") 

```




