---
title: "model_development"
output: html_document
---

```{r}
# Load the datasets
load(paste0(data_folder, "abiotic_quadrat.RData"))
load(paste0(data_folder, "abiotic_filterpaper.RData"))
load(paste0(data_folder, "abiotic_canopycover.RData"))
load(paste0(data_folder, "abiotic_penetrometer.RData"))
load(paste0(data_folder, "hobo_rq2.RData"))

```

```{r}
# Create 6 hour intervals for time series graphs
start <- as.POSIXct(strptime("2017-09-25 04:00:00", "%Y-%m-%d %H:%M:%S"))
interval <- 60*6
end <- start + as.difftime(4, units="days")
labels = seq(from=start, by=interval*60, to=end)

# Create just the time intervals instead, since shading is used for days
start2 <- as.POSIXct(strptime("2017-09-25 18:00:00", "%Y-%m-%d %H:%M:%S"))
end2 <- start + as.difftime(5, units="days")
labels2 = seq(from=start2, by=interval*60, to=end2)
time_labels = format(labels2, format = "%H:%M:%S")

labels = labels[2:17]
time_labels <- substr(time_labels[2:17], 1, 5)

# Filter the data between useable dates
datarq2 <- hobo_rq2.df # Ten Hour Lag..


# Get shading for different days
hobo_days <- data.frame(startday = c(as.POSIXct(strftime("2017-09-26 3:00:01", "%Y-%m-%d %H:%M:%S")),
                                     as.POSIXct(strftime("2017-09-26 00:00:00", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-27 00:00:00", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-28 00:00:00", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins")),
                        endday =   c(as.POSIXct(strftime("2017-09-25 23:59:59", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-26 23:59:59", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-27 23:59:59", "%Y-%m-%d %H:%M:%S"))+as.difftime(60*10, units="mins"),
                                     as.POSIXct(strftime("2017-09-28 22:00:00", "%Y-%m-%d %H:%M:%S")))) %>%
                        mutate(day = c("Monday", "Tuesday", "Wednesday", "Thursday"),
                               day = factor(day,
                                            levels = c("Monday", "Tuesday", "Wednesday", "Thursday"),
                                            ordered = TRUE)) %>% 
  tbl_df()

# Show filter point for late hobos
min_new_time <- as.POSIXct(strftime("2017-09-28 03:00:00", "%Y-%m-%d %H:%M:%S"))

latehobos <- data.frame(ytemp = c(25.5, 28),
                        xdatetime = c(min_new_time, min_new_time)) %>%
  tbl_df
```

The temperature analysis is limited to predictor variables summarised at the transect level. This provides only six different measurements, which essentially captures the variation between transects. Thus, only the difference between disturbed and pristine forest areas are reported.

### Site: Time Series
The figure below compares the recorded temperature over time, with the green and red points representing the pristine and disturbed areas. 

```{r}
# Plot the graphs
ggplot() +
  theme_project() +
  scale_x_datetime(breaks = labels
                   ,labels = time_labels
                   ) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1)) +
  geom_rect(aes(xmin=startday, xmax=endday, ymin = 25.5, ymax = 28, fill = day),
            data = hobo_days, alpha = 0.4)   +
  scale_fill_tableau(name = "Day")+
  geom_point(aes(x=date_time, y=temp, col=site),
             data = datarq2, size=1) +
  scale_colour_manual(name = "Site",
                      values = colours.site) +
  ggtitle("Temperature over Time") +
  xlab("Time of Day") +
  ylab("Temperature (Degrees Celsius)") +
  geom_line(aes(x=xdatetime, y=ytemp),
            data = latehobos)

# ggsave(paste0(data_folder, "temp_timeseries.png"), width = 6, height = 3.5, dpi = 900)
```

With a limited number of days recorded, the data is combined by their 24 hour time, to increase the number of observations. The figure below demonstrates the relationship between time of day and temperature.

```{r}
# Filter the data between useable dates
datarq2 <- hobo_rq2.df # Ten Hour Lag..

datarq2 %<>%
  mutate(time24 = as.numeric(substr(date_time, 12, 13)) + 
                         as.numeric(substr(date_time, 15, 16))/60)

# Plot the graphs
ggplot() +
  theme_project() +
  scale_fill_tableau(name = "Day")+
  geom_point(aes(x=time24, y=temp, col=site),
             data = datarq2, size=1) +
  scale_colour_manual(name = "Site",
                      values = colours.site) +
  ggtitle("Temperature over 24 Period") +
  xlab("Hour") +
  scale_x_continuous(breaks = seq(0, 24, 6)) +
  ylab("Temperature (Degrees Celsius)")


```

We can see that disturbed transects tend to have a higher tmperature accross the two and a half day cycle. An interesting 'spike' in the data is observed for one pristine transect between 12pm and 6pm. The source of this measurment is unknown, so can not be excluded as an outlier.


<!-- ### Univariate Relationship -->
<!-- ```{r} -->

<!-- # Decopmosition -->
<!-- ggplot() +  -->
<!--   geom_point(aes(x=site, y=decomposition, col = site), -->
<!--        data = abiotic_filterpaper.df) + -->
<!--   geom_boxplot(aes(x=site, y=decomposition, col = site), -->
<!--        data = abiotic_filterpaper.df)+ -->
<!--   ggtitle("Decomposition") + -->
<!--   xlab("Site") + -->
<!--   ylab("Decomposition Rate (grams/days)") + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site) + -->
<!--   theme(legend.background = element_rect(bg_green), -->
<!--         legend.box.background = element_rect(fill=bg_green, color=bg_green), -->
<!--         legend.key = element_rect(fill=bg_green), -->
<!--         plot.background = element_rect(bg_green, color=bg_green)) + -->
<!--   geom_abline(slope = 0, intercept = 0) -->

<!-- # LAI -->
<!-- ggplot(aes(x=site, y=lai, col = site), -->
<!--        data = abiotic_canopycover.df) +  -->
<!--   geom_point() + -->
<!--   geom_boxplot() + -->
<!--   ggtitle("Leaf Area Index") + -->
<!--   theme_project()+ -->
<!--   scale_colour_manual(values = colours.site) + -->
<!--   xlab("Site") + -->
<!--   ylab("Leaf Area Index") + -->
<!--   theme(legend.background = element_rect(bg_green), -->
<!--         legend.box.background = element_rect(fill=bg_green, color=bg_green), -->
<!--         legend.key = element_rect(fill=bg_green), -->
<!--         plot.background = element_rect(bg_green, color=bg_green)) -->


<!-- # Compaction -->
<!-- ggplot(aes(x=site, y=compaction, col = site), -->
<!--        data = abiotic_penetrometer.df) +  -->
<!--   geom_boxplot() + -->
<!--   ggtitle("Penetrometer") + -->
<!--   theme_project()+ -->
<!--   scale_colour_manual(values = colours.site) + -->
<!--   xlab("Site") + -->
<!--   ylab("Compaction (pressure)") + -->
<!--   theme(legend.background = element_rect(bg_green), -->
<!--         legend.box.background = element_rect(fill=bg_green, color=bg_green), -->
<!--         legend.key = element_rect(fill=bg_green), -->
<!--         plot.background = element_rect(bg_green, color=bg_green)) -->

<!-- ``` -->

<!-- # Bivariate Relationships -->
<!-- ```{r} -->
<!-- ## Abiotic variables -->
<!-- abiotic_vars <- c("av_quad_compaction", "av_trans_decomposition", "min_temp", "max_temp", "range_temp", "av_quad_lai", "av_quad_gft") -->


<!-- abiotic_quadrat.df %>%  -->
<!--   select(one_of(abiotic_vars)) %>% -->
<!--   cor() %>% -->
<!--   round(digits=2) -->

<!-- abiotic_vars2 <- c("av_quad_compaction", "av_trans_decomposition", "max_temp", "av_quad_lai") -->

<!-- abiotic_quadrat.df %>%  -->
<!--   select(one_of(abiotic_vars2)) %>% -->
<!--   cor() %>% -->
<!--   round(digits=2) -->

<!-- # correlation results -->
<!-- # elevation will account for decopmosition and min_temperature, however we will leave compaction in the model for now as it is at the quadrat level and may provide additional information -->
<!-- # range_temp will account for max_temp -->
<!-- # so model elevation, range_temp, compaction, lai -->

<!-- abiotic_quadrat.df %>% -->
<!--   ggplot(aes(x=av_trans_elevation, y=av_quad_compaction)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se = FALSE)+ -->
<!--   theme_project()+ -->
<!--   scale_colour_tableau() + -->
<!--   xlab("Elevation (m)") + -->
<!--   ylab("Compaction (pressure)") + -->
<!--   ggtitle("Compaction vs Elevation") -->

<!-- abiotic_quadrat.df %>% -->
<!--   ggplot(aes(x=av_trans_elevation, y=av_trans_decomposition)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se = FALSE)+ -->
<!--   theme_project()+ -->
<!--   scale_colour_tableau() + -->
<!--   xlab("Elevation (m)") + -->
<!--   ylab("Decomposition") + -->
<!--   ggtitle("Compaction vs Decomposition") -->

<!-- abiotic_quadrat.df %>% -->
<!--   mutate(av_quad_lai = ifelse(av_quad_lai == disturbed_mean_lai, NA, av_quad_lai)) %>% -->
<!--   ggplot(aes(x=av_trans_elevation, y=av_quad_lai)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se = FALSE)+ -->
<!--   theme_project()+ -->
<!--   scale_colour_tableau() + -->
<!--   xlab("Elevation (m)") + -->
<!--   ylab("Leaf Area Index") + -->
<!--   ggtitle("Elevation vs LAI (NA's)") -->

<!-- abiotic_quadrat.df %>% -->
<!--   # mutate(av_quad_lai = ifelse(av_quad_lai == disturbed_mean_lai, NA, av_quad_lai)) %>% -->
<!--   ggplot(aes(x=av_trans_elevation, y=av_quad_lai)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se = FALSE)+ -->
<!--   theme_project()+ -->
<!--   scale_colour_tableau() + -->
<!--   xlab("Elevation (m)") + -->
<!--   ylab("Leaf Area Index") + -->
<!--   ggtitle("Elevation vs LAI (Imputed)") -->

<!-- abiotic_quadrat.df %>% -->
<!--   # mutate(av_quad_lai = ifelse(av_quad_lai == disturbed_mean_lai, NA, av_quad_lai)) %>% -->
<!--   ggplot(aes(x=max_temp, y=av_quad_lai)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se = FALSE)+ -->
<!--   theme_project()+ -->
<!--   scale_colour_tableau() + -->
<!--   xlab("Max Temperature") + -->
<!--   ylab("Leaf Area Index") + -->
<!--   ggtitle("Max Temperature vs LAI (Imputed)") -->
<!-- ``` -->


