---
title: "model_development"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_datasets_exploratory_analysis}
# This code should be removed when entire process is productionised
dropbox <- "C:\\Users\\Jacob\\Dropbox\\Semester 2 2017\\MXB344\\Project\\Data\\"

load(paste0(dropbox, "domseedlingcover_rq1.RData"))
load(paste0(dropbox, "domshannons_rq1.RData"))
load(paste0(dropbox, "domsla_rq1.RData"))
load(paste0(dropbox, "species_richness_rq3.RData"))
load(paste0(dropbox, "hobo_rq2.RData"))
```

This section provides an insight to the trends in the collected data. This analysis will be focused on individual research questions. This will provide interpretability when developing the statistical model.

## Research Question 1: Dominant Species Seedling Cover
```{r}
domseedlingcover_rq1.df

```

### Site vs Dominant Seedling Cover
In the figure below, we observe:

  * a slighty larger variance for domiannt species 1 and 2 in pristine sites.
  * higher IQR and medians for dominant species 1 and 2 in pristine sites
  * domiant species 3 is less evident in pristine sites
  * the coverage dominant species 4 is insignificant in comparison to the other 3
  
```{r}
domseedlingcover_rq1.df %>%
  select(dom_species_id, site, dom_seedling_cover, transect, quadrat) %>%
  distinct() %>%
  filter(!is.na(dom_species_id)) %>%
  ggplot(aes(x = factor(dom_species_id), y = dom_seedling_cover, col = site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_tableau() +
  ggtitle("Dominant Seedling Cover vs Site")

```




## Research Question 1: Dominant Species Shannons index of Diversity
```{r}
domshannons_rq1.df %>% str()
```

```{r}



```


## Research Question 1: Dominant Species Specific Leaf Area
```{r}
dataq3 <- domsla_rq1.df
```

  * leaf area - photosynthetic aparatus of the plant
  * amount of investment of dry matter (plant investment into growth defence trade off) -> Most dominant species most compettitive, higher specific leaf area


```{r}
dataq3 %>%
  ggplot(aes(x=factor(dom_species_id), y = dom_sla, col=site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_tableau() +
  ggtitle("SLA vs Site and Dominant Species ID")

```


## Abiotic
```{r}
penetrometer2 %>% ggplot(aes(x=Site, y=Compaction)) + geom_boxplot()

filter_paper2 %>% ggplot(aes(x=Site, y=decomposition)) + geom_boxplot()

canopy_cover2 %>% ggplot(aes(x=Site, y=decomposition)) + geom_boxplot()


```

## Leaf Traits
```{r}
specieslvl_dom_seedling_count2 %>%
  left_join

leaf_traits2 %>%
  ggplot(aes)


```




