---
title: "model_development"
output: html_document
---

```{r load_datasets_exploratory_analysis}
# This code should be removed when entire process is productionised
dropbox <- "C:\\Users\\Jacob\\Dropbox\\Semester 2 2017\\MXB344\\Project\\Data\\"

load(paste0(dropbox, "domsla_rq1.RData"))

```

  * leaf area - photosynthetic aparatus of the plant
  * amount of investment of dry matter (plant investment into growth defence trade off) -> Most dominant species most compettitive, higher specific leaf area

### Abundance-Weighted SLA vs Site
```{r}
domsla_rq1.df %>%
  ggplot(aes(x=site, y = dom_sla_weighted_abundance)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_tableau() +
  ggtitle("Weighted SLA vs Site")+
  xlab("Site") +
  ylab("Abundance-Weighted SLA")

```

### Abundance-Weighted SLA vs Dominant Species ID
```{r}
domsla_rq1.df %>%
  ggplot(aes(x=dom_species_id, y = dom_sla_weighted_abundance, col=site)) +
  geom_boxplot() +
  theme_project() +
  ggtitle("Weighted SLA vs Site and Dominant Species ID")+
  xlab("Dominant Species") +
  ylab("Abundance-Weighted SLA") +
  scale_colour_manual(values = colours.site)

```

### Abundance-Weighted SLA vs Elevation
```{r}
domsla_rq1.df %>%
  ggplot(aes(x=(round(av_trans_elevation)), y = dom_sla_weighted_abundance, col=site)) +
  geom_point() +
  theme_project() +
  ggtitle("Weighted SLA vs Elevation")+
  xlab("Transect Elevation") +
  ylab("Abundance-Weighted SLA") +
  scale_colour_manual(name = "Site",
                      values = colours.site)

domsla_rq1.df %>%
  ggplot(aes(x=paste0(site, ":", 
                      round(av_trans_elevation), "m"), 
             y = dom_sla_weighted_abundance,
             col=dom_species_id)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_tableau() +
  ggtitle("Weighted SLA vs Elevation")+
  xlab("Transect Elevation") +
  ylab("Abundance-Weighted SLA")
```


### Functional Diversity: Abundance vs SLA
```{r}
# dataq3 %>%
#   ggplot(aes(dom_sla, col = dom_species_id)) +
#   geom_density()

slagroup.df <- domsla_rq1.df %>%
  mutate(sla_group = cut(dom_sla,
                         breaks = seq(0, max(dom_sla), 25))) %>%
  group_by(dom_species_id, sla_group) %>%
  # summarise(sla_group_abundance = sum(dom_abundance)) %>% # Incorrect logic here.. since they all have the same abundance ata  quadrat level
  summarise(obs = n()) %>%
  mutate(index = as.numeric(sla_group)) %>%
  arrange(index)


slagroup.df %>%
  ggplot(aes(x=index, y = obs, 
             fill = dom_species_id, col = dom_species_id)) +
  # geom_bar(stat = "identity", position = "dodge") +
  geom_point() +
  geom_smooth(span = 0.4) +
  theme_project() +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1))  +
  ggtitle("Functional Evenness of SLA for Dominant Species") +
  ylab("Number of Leaf Samples") +
  xlab("Bucketed SLA") +
  # scale_fill_tableau(name = "Dominant Species") +
  scale_colour_tableau(name = "Dominant Species") +
  scale_x_continuous(breaks = unique(slagroup.df$index),
                     labels = unique(slagroup.df$sla_group),
                     lim  = c(1, 15))
  

# slagroup.df$index %>% unique

```

### SLA vs Species Richness
```{r}
domsla_rq1.df %>%
  ggplot(aes(x = species_richness, y = dom_sla_weighted_abundance, 
             col = site)) +
  geom_point(size = 1) +
  theme_project() +
  scale_colour_manual(name = "Site", values = colours.site) +
  ggtitle("Domiant Species: SLA vs Species Richness (12 Quadrats)") +
  xlab("Species Richness") +
  ylab("Abundance-Weighted SLA") +
  facet_wrap("dom_species_id")


```

### SLA vs Dominant Species Leaf Traits
```{r}
leaf_trait_choice <- "leaf_arrangement"

domsla_rq1.df %>%
  select(dom_sla)


```

