---
title: "model_development"
output: html_document
---


``` {r}
library(car)
#relabel domseedlingcover_rq1
domseedlingcover <- domseedlingcover_rq1.df

## omit NA
# domseedlingcover <- na.omit(domseedlingcover)


# Setting variables as factors
domseedlingcover$site <- as.factor(domseedlingcover$site)
domseedlingcover$transect <- as.factor(domseedlingcover$transect)
domseedlingcover$quadrat <- as.factor(domseedlingcover$quadrat)
domseedlingcover$dom_species_id <- as.factor(domseedlingcover$dom_species_id)

#converting % into decimal for overall seedling cover and logged
domseedlingcover<-mutate(domseedlingcover,
                         overallseedlingcover = log(overall_seedling_cover/100))

#mutate site_trans
domseedlingcover <- mutate(domseedlingcover,
                           site_trans = factor(paste0(domseedlingcover$site,
                                                      domseedlingcover$transect)))

#scale factors
domseedlingcover$dom_abundance <- scale(domseedlingcover$dom_abundance, center=TRUE, scale=TRUE)
domseedlingcover$overallseedlingcover<- scale(domseedlingcover$overallseedlingcover, center=TRUE, scale=TRUE)
domseedlingcover$av_dom_sla_from_ind <- scale(domseedlingcover$av_dom_sla_from_ind, center=TRUE, scale=TRUE)
domseedlingcover$av_dom_sla_from_total <- scale(domseedlingcover$av_dom_sla_from_total, center  =TRUE, scale=TRUE)
domseedlingcover$av_quad_compaction <- scale(domseedlingcover$av_quad_compaction, center =TRUE, scale=TRUE)
domseedlingcover$av_trans_elevation <- scale(domseedlingcover$av_trans_elevation, center=TRUE, scale=TRUE)
domseedlingcover$av_trans_decomposition <- scale(domseedlingcover$av_trans_decomposition, center = TRUE, scale=TRUE)
domseedlingcover$min_temp <- scale(domseedlingcover$min_temp, center=TRUE, scale=TRUE)
domseedlingcover$max_temp <- scale(domseedlingcover$max_temp, center=TRUE, scale =TRUE)

#rewriting 0 of dom_Seedling_cover as 0.000000001
domseedlingcover$dom_seedling_cover[domseedlingcover$dom_seedling_cover==0] <- 0.000000000001


#creating variable r = logit(dom_seedling_cover/100)
#commencing logistic regression
domseedlingcover <- mutate(domseedlingcover, r = logit(dom_seedling_cover/100))

#Checking correlation. Removing factors, humidity, hobo times, 
# remove correlating factors too
df = subset(domseedlingcover, select = -c(`site`, `transect`, `quadrat`, `dom_species_id`,
                                          `av_dom_sla_from_ind`, `total_dom_leaf_area`,
                                          `dom_seedling_cover`, `site_trans`))

```

The exploratory graphs investigated for this regression are with site, abundance, and species ID. Each predictor variable was evaluated separately, as well as some variables being evaluated as an interaction. The interactions considered were: site & species ID, abundance & species ID. 

#### Abundance
With the species cover and the species abundance, it can be seen that there is a vague but still noticeable upward trend. Between each species there appears to be differences in their trend line slopes, but their interaction was not significant in the final model fit. 

```{r}
domseedlingcover %>%
  ggplot(aes(x=dom_abundance, 
             y = r,
             col=dom_species_id)) +
  geom_point()  +
  geom_smooth(method="glm",se=FALSE, span = 5) +
  theme_project()+
  scale_colour_tableau(name = "Dominant Species ID") +
  ggtitle("(Transformed) Seedling Cover vs (Scaled) Species Abundance")+
  xlab("(Scaled) Species Abundance") +
  ylab("(Transformed)Seedling Cover")

```

#### Site
With the range, interquartile range, and median values being very similar, the difference between the two disturbance sites does not seem to be significant on inspection. It appears that both disturbance sites exhibit similar outputs of seedling cover. However, for the sake of this project and the premise of our research question, it will be verified whether the disturbance truly have an effect on the seedling cover. 

```{r}
domseedlingcover %>%
  ggplot(aes(x=site, y = r, col=site)) +
  geom_boxplot() +
  scale_colour_manual(values = colours.site, name = "Site") +
  theme_project() +
  ggtitle("(Transformed) Seedling Cover vs Site")+
  xlab("Site") +
  ylab("(Transformed) Seedling Cover")

```


#### Species
From inspection, it is clear that there is significant differences in which the different species contribute to the seedling cover. It is also to be noted that within each species ID, there is notable differences between the disturbance sites. However, due to the model fit procedure, the interaction between species ID and site was not considered. 

```{r}
domseedlingcover %>%
  ggplot(aes(x=dom_species_id, 
             y = r,
             col=site)) +
  geom_boxplot()  +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("(Transformed) Seedling Cover vs Species ID")+
  xlab("Species ID") +
  ylab("(Transformed) Seedling Cover")


```


#### Correlation


