---
title: "model_development"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Model Design

  * Model design is based of experimental design
    * Random effects structure is quadrats nested in transects
  * Primary modelling approach is bayesian, with the INLA package. This implements a Laplace approximation to the posterior distribution of the estimate parameters.
    * Effective when parameter estimates follow a Gaussian distribution (normally distributed)
    * Computationally efficient
    * WHY IS BAYESIAN SO GOOD FOR ECOLOGY?
    
The model development section is organised as follows. Five models will be developed and evaluated in the next five sections, relating to different aspects of the research questions. These five models correspond to the five data sets summarised in the Data Build section. Each sub-model development will include:

  1. Assessment of predictors that maximise the marginal log-likehood.
  2. Summary of credible intervals of parameter estimates.
  3. MODEL FIT?
  4. Brief summary comparison to the results from a frequentist approach with confidence intervals.


```{r load_datasets}
dropbox <- "C:\\Users\\Jacob\\Dropbox\\Semester 2 2017\\MXB344\\Project\\"

load(paste0(dropbox, "quadrat_modelling.RData"))
load(paste0(dropbox, "species_modelling.RData"))
load(paste0(dropbox, "species_rawabiotic_modelling.RData"))
load(paste0(dropbox, "hobo_modelling.RData"))
```


```{r}
library(nlme)
library(lme4)

# Run regular lme on log(dom_shannon)
fit <- lme(log(dom_shannon) ~ site, 
           random = ~1|transect/quadrat,
           data = species_modelling.df,
           method = "REML")

summary(fit)

# SiteP is significant. intercept -0.515, coefficient - 0.133
# Compare to gaussian glmm in fit2
fit.2 <- glmer(log(dom_shannon) ~ site + (1|transect/quadrat),
             data = species_modelling.df,
             family = "gaussian")

summary(fit.2)

# Can get the variance estimates in glmer
coefficients(fit.2)

# glmer produces the same coefficients! but no p-values?
# can get p values from t values, but can't get degrees of freedom easily..
p_value = 2*pt(t_value, df=133, lower=FALSE)


# Test the same lme model with the large combined dataset
fit.1 <- lme(log(dom_shannon) ~ site, 
           random = ~1|transect/quadrat,
           data = species_rawabiotic_modelling.df,
           method = "REML")

summary(fit.1)

#as expected, the estimates change between datasets.
# I thought the estimates should be the same, with less standard errrors?
# Check balance of datasets
species_modelling.df %>%
  group_by(site, transect, quadrat, dom_shannon) %>%
  summarise(obs = n()) %>%
  left_join(
    species_rawabiotic_modelling.df %>%
  group_by(site, transect, quadrat, dom_shannon) %>%
  summarise(big_obs = n()),
  by = c("site", "transect", "quadrat", "dom_shannon")
  ) %>%
  data.frame()

# as expected, the joining of datasets produces unbalance. 
# This is due to some species occuring more often in some datasets
# so, we need to exclude quadrat level data from species lvl data, since this creates 'made up' replicates of single observations


# When we plot both datasets, they look exactly the same.
# But the box_plots will change... hmmm...
# species_rawabiotic_modelling.df %>%
species_modelling.df %>%
  ggplot(aes(x=site, y = log(dom_shannon))) +
  geom_point()

# In conlcusion, different dataset for every different level
# When observations cannot be matched, we must combine them at the min, mean, median, max level.


# Another example, use a repeated quadrat_modelling.df datset
# with a balanced dataset repeated, effect estimates are equivalent.
fit.5 <- lme(log(dom_shannon) ~ Site, 
             random = ~1|Transect/Quadrat,
             data = quadrat_modelling.df)
summary(fit.5)

fit.6 <- lme(log(dom_shannon) ~ Site, 
             random = ~1|Transect/Quadrat,
             data = rbind(quadrat_modelling.df,
                          quadrat_modelling.df))
summary(fit.6)

```


```{r}


fit2 <- glmer(dom_abundance ~ site + (1|transect/quadrat),
             data = species_modelling.df,
             family = "poisson")

summary(fit2)




```

```{r}
# install.packages("INLA", repos="https://inla.r-inla-download.org/R/stable")
# options(repos = c(getOption("repos"), INLA="https://inla.r-inla-download.org/R/testing"))
# update.packages("INLA")
library(INLA)
#### Fit the model via INLA
fit3 = inla(log(dom_shannon) ~ site + f(transect, model="iid") + f(quadrat:transect, model = "iid"),
            family="gaussian",
            data=quadrat_modelling.df)
summary(fit3)



#result = inla(formula,family="gaussian",data=data.full,control.compute =list(dic=TRUE, waic= TRUE, cpo = TRUE, mlik = TRUE,config=TRUE), control.predictor=list(compute=T))

```
