---
title: "model_development"
output: html_document
---

```{r}
# This code should be removed when entire process is productionised
dropbox <- "C:\\Users\\Jacob\\Dropbox\\Semester 2 2017\\MXB344\\Project\\Data\\"

load(paste0(dropbox, "domseedlingcover_rq1.RData"))

```

This section provides an insight to the trends in the collected data. This analysis will be focused on individual research questions. This will provide interpretability when developing the statistical model.



All about light

  * Competitive domiance
  * High cover, low frquency -> big leaves when young
  * life history strategy -> not just maximise 
  
  * Ecophyisiology
  * plant plasticity: intra specific variability -> more variability = better adaptation to more environment. More adaptation to different -> Measure of variation
  * Incorporate adaptation: CV = mean/variance
    * High variaation in leaf traits -> Use grime paper : 


```{r}
domseedlingcover_rq1.df

```

#### Site vs Dominant Seedling Cover
In the figure below, we observe:

  * a slighty larger variance for domiannt species 1 and 2 in pristine sites.
  * higher IQR and medians for dominant species 1 and 2 in pristine sites
  * domiant species 3 is less evident in pristine sites
  * the coverage dominant species 4 is insignificant in comparison to the other 3
  
```{r}
domseedlingcover_rq1.df %>%
  select(dom_species_id, site, dom_seedling_cover, transect, quadrat) %>%
  distinct() %>%
  filter(!is.na(dom_species_id)) %>%
  ggplot(aes(x = factor(dom_species_id), y = dom_seedling_cover)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_tableau() +
  ggtitle("Dominant Seedling Cover vs Site")

```

#### Dominant Seedling Cover vs Elevation
```{r}
domseedlingcover_rq1.df  %>%
  ggplot(aes(x=factor(round(av_trans_elevation)), 
             y = dom_seedling_cover, 
             col=dom_species_id)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_tableau() +
  ggtitle("Seedling Cover vs Elevation")+
  xlab("Transect Elevation") +
  ylab("Seedling Cover (%)")


```


#### Dominant Seedling Abundance vs Elevation
```{r}
domseedlingcover_rq1.df  %>%
  ggplot(aes(x=factor(round(av_trans_elevation)), 
             y = dom_abundance, 
             col=dom_species_id)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_tableau() +
  ggtitle("Seedling Abundance vs Elevation")+
  xlab("Transect Elevation") +
  ylab("Seedling Abundance")


```