---
title: "model_development"
output: html_document
---

```{r, include=FALSE}

#Setup data

# head(domshannons_rq1.df)
# attach(domshannons_rq1.df)

#FACTOR 
domshannons_rq1.df$transect <- as.factor(domshannons_rq1.df$transect)
domshannons_rq1.df$quadrat <- as.factor(domshannons_rq1.df$quadrat)

#SCALE VARIABLES - ONLY RUN ONCE! - KEEP RESPONSE THE SAME AND COMPARABLE
    domshannons_rq1.df$dom_total_abundance <- scale(domshannons_rq1.df$dom_total_abundance, center=TRUE, scale=TRUE)
            domshannons_rq1.df$dom_simpson <- scale(domshannons_rq1.df$dom_simpson, center=TRUE, scale=TRUE)
domshannons_rq1.df$dom_total_seedling_cover <- scale(domshannons_rq1.df$dom_total_seedling_cover, center=TRUE, scale=TRUE)
  domshannons_rq1.df$overall_seedling_cover <- scale(domshannons_rq1.df$overall_seedling_cover, center=TRUE, scale=TRUE)
      domshannons_rq1.df$total_dom_leaf_area <- scale(domshannons_rq1.df$total_dom_leaf_area, center=TRUE, scale=TRUE)
domshannons_rq1.df$total_dom_leaf_dry_weight <- scale(domshannons_rq1.df$total_dom_leaf_dry_weight, center=TRUE, scale=TRUE)
         domshannons_rq1.df$av_totaldom_sla <- scale(domshannons_rq1.df$av_totaldom_sla, center=TRUE, scale=TRUE)
            domshannons_rq1.df$av_dom_1_sla <- scale(domshannons_rq1.df$av_dom_1_sla, center=TRUE, scale=TRUE)
             domshannons_rq1.df$av_dom_2_sla <- scale(domshannons_rq1.df$av_dom_2_sla, center=TRUE, scale=TRUE)
             domshannons_rq1.df$av_dom_3_sla <- scale(domshannons_rq1.df$av_dom_3_sla, center=TRUE, scale=TRUE)
      domshannons_rq1.df$av_quad_compaction <- scale(domshannons_rq1.df$av_quad_compaction, center=TRUE, scale=TRUE)
           domshannons_rq1.df$av_quad_lai <- scale(domshannons_rq1.df$av_quad_lai, center=TRUE, scale=TRUE)
           domshannons_rq1.df$av_quad_gft <- scale(domshannons_rq1.df$av_quad_gft, center=TRUE, scale=TRUE)
      domshannons_rq1.df$av_trans_elevation <- scale(domshannons_rq1.df$av_trans_elevation, center=TRUE, scale=TRUE)
  domshannons_rq1.df$av_trans_decomposition <- scale(domshannons_rq1.df$av_trans_decomposition, center=TRUE, scale=TRUE)
                domshannons_rq1.df$min_temp <- scale(domshannons_rq1.df$min_temp, center=TRUE, scale=TRUE)
                domshannons_rq1.df$max_temp <- scale(domshannons_rq1.df$max_temp, center=TRUE, scale=TRUE)
                domshannons_rq1.df$range_temp <- scale(domshannons_rq1.df$range_temp, center=TRUE, scale=TRUE)

domshannons_rq1.df %<>% mutate(site_trans = factor(paste0(site, transect)))               
                


```


#### Random Effect
The figure below shows that there is variability between the transects. For an unknown reason, INLA is unable to calulate this - which is why our random effects presented to explain so little of the variance. This may be due to the sample size and that the fixed effects are able to explain a majority of the variation.


```{r}

rand_eff_p <- ggplot(aes(x=site_trans, y=dom_shannon, col=site), data=domshannons_rq1.df) + geom_boxplot() + 
  labs(title="Shannon's Index vs. Transect", x="Random Effect / Transect", y= "Shannon's Index") + scale_colour_manual(values = colours.site, name = "Site") + theme_project(); rand_eff_p


```

#### Site
Looking at Shannon's Diversity Index in the figure below, it was clear there was no difference between sites. Although there was more variability in the  disturbed sites. 

To further determine what other factors may influence Shannon's Index, exploratory graphs will determine which variables, and their interactions among sites, may be able to model Shannon's Index. 
```{r, fig.align='center'}

#Site
a_p <- ggplot(aes(x=site, y=dom_shannon, col=site), data=domshannons_rq1.df) + geom_boxplot() + labs(title="Shannon's Index of Biodiversity Across Sites", y="Shannon Index (scaled)", x="Site") + geom_smooth(method = "lm") + scale_colour_manual(values = colours.site, name = "Site") + theme_project(); a_p

  
```
<!-- FIGURE #1: The distrubution of shannon's index between the disturbed and pristine transects.  -->

The figure below shows that total dominant abundance, overall seedling cover, dominant total leaf area, total dominant leaf dry weight, and average quadrat GFT appear to have a relationship with Shannon's Index. This is based on the inspecting the standard error and the data that falls within the confidence interval.  

```{r, fig.align='center', fig.height=5, fig.width=7}

#dom_total_abundance
d_p <- ggplot(aes(y=dom_shannon, x=dom_total_abundance), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. v. T. D. Abund", y="Shannon Index", x="dom_total_abundance (scaled)") + geom_smooth(method = "lm") + theme_project()

#dom_simpson
e_p <- ggplot(aes(y=dom_shannon, x=dom_simpson), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Simpson's Ind", y="Shannon Index", x="dom_simpson (scaled)") + geom_smooth(method = "lm") + theme_project()

#dom_total_seedling_cover
f_p <- ggplot(aes(y=dom_shannon, x=dom_total_seedling_cover), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Tot Seed Cover", y="Shannon Index", x="dom_total_seedling_cover (scaled)") + geom_smooth(method = "lm") + theme_project()

#overall_seedling_cover
g_p <- ggplot(aes(y=dom_shannon, x=overall_seedling_cover), data=domshannons_rq1.df) + geom_point() + labs(title=" S.I. v. Ov Seed Cov", y="Shannon Index", x="overall_seedling_cover (scaled)") + geom_smooth(method = "lm") + theme_project()

#total_dom_leaf_area
h_p <- ggplot(aes(y=dom_shannon, x=total_dom_leaf_area), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. v. D. Leaf Area", y="Shannon Index", x="total_dom_leaf_area (scaled)") + geom_smooth(method = "lm") + theme_project()


#total_dom_leaf_dry_weight
i_p <- ggplot(aes(y=dom_shannon, x=total_dom_leaf_dry_weight), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. v. D. Leaf Dry", y="Shannon Index", x="total_dom_leaf_dry_weight (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_totaldom_sla
j_p <- ggplot(aes(y=dom_shannon, x=av_totaldom_sla), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Avg SLA", y="Shannon Index", x="av_totaldom_sla (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_dom_1_sla
k_p <- ggplot(aes(y=dom_shannon, x=av_dom_1_sla), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Sp. 1 Avg SLA", y="Shannon Index", x="av_dom_1_sla (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_dom_2_sla
l_p <- ggplot(aes(y=dom_shannon, x=av_dom_2_sla), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Sp. 2 Avg SLA", y="Shannon Index", x="av_dom_2_sla (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_dom_3_sla
m_p <- ggplot(aes(y=dom_shannon, x=av_dom_3_sla), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Sp. 3 Avg SLA", y="Shannon Index", x="av_dom_3_sla (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_quad_compaction
n_p <- ggplot(aes(y=dom_shannon, x=av_quad_compaction), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. v. Avg Quad Comp", y="Shannon Index", x="av_quad_compaction (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_quad_lai
o_p <- ggplot(aes(y=dom_shannon, x=av_quad_lai), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Avg Quad LAI", y="Shannon Index", x="av_quad_lai (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_quad_gft
p_p <- ggplot(aes(y=dom_shannon, x=av_quad_gft), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. v. Avg Qua GFT", y="Shannon Index", x="av_quad_gft (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_trans_elevation
q_p <- ggplot(aes(y=dom_shannon, x=av_trans_elevation), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Avg Trans El", y="Shannon Index", x="av_trans_elevation (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_trans_decomposition
r_p <- ggplot(aes(y=dom_shannon, x=av_trans_decomposition), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Avg Tran Decomp", y="Shannon Index", x="av_trans_decomposition (scaled)") + geom_smooth(method = "lm") + theme_project()

#min_temp
s_p <- ggplot(aes(y=dom_shannon, x=min_temp), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Min Temp", y="Shannon Index", x="min_temp (scaled)") + geom_smooth(method = "lm") + theme_project()

#max_temp
t_p <- ggplot(aes(y=dom_shannon, x=max_temp), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Max Temp", y="Shannon Index", x="max_temp (scaled)") + geom_smooth(method = "lm") + theme_project()

#range_temp
u_p <- ggplot(aes(y=dom_shannon, x=range_temp), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Range of Temp", y="Shannon Index", x="range_temp (scaled)") + geom_smooth(method = "lm") + theme_project()


multiplot(d_p, g_p, h_p, i_p, p_p,
          layout = matrix(c(1,2,3,4,5,6), nrow=2))

```

<!-- FIGURE #2: (a) Scaled total dominant species against scaled shannon's diversity Index. (b) Scaled overal seedling cover against scaled shannon's diversity index. (c) Scaled total dominant leaf area against scaled shannon's diversity index. (d)Scaled total dominant leaf dry weight against scaled shannon's diversity index. (e) Scaled avergae quadrat GFT against scaled shannon's diversity index. -->


Figure #3, portrays a difference between site with total dominant species abundance and overall seedling cover. These interactions will be added to the modelling along with the predictor variables above (Figure #2).

```{r, fig.align='center'}

{

#dom_total_abundance
d_pp <- ggplot(aes(y=dom_shannon, x=dom_total_abundance, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="(a) S.I. vs Tot Dom Abundance", y="Shannon Index", x="dom_total_abundance (scaled)") + geom_smooth(method = "lm") + theme_project() + scale_colour_manual(values = colours.site)

#dom_simpson
e_pp <- ggplot(aes(y=dom_shannon, x=dom_simpson, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Simpson's Ind", y="Shannon Index", x="dom_simpson (scaled)") + geom_smooth(method = "lm") + theme_project()

#dom_total_seedling_cover
f_pp <- ggplot(aes(y=dom_shannon, x=dom_total_seedling_cover, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Tot Seed Cover", y="Shannon Index", x="dom_total_seedling_cover (scaled)") + geom_smooth(method = "lm") + theme_project()

#overall_seedling_cover
g_pp <- ggplot(aes(y=dom_shannon, x=overall_seedling_cover, col=site), data=domshannons_rq1.df) + geom_point() + labs(title=" (b) S.I. vs Overall Seed Cover", y="Shannon Index", x="overall_seedling_cover (scaled)") + geom_smooth(method = "lm") + theme_project()+ scale_colour_manual(values = colours.site)

#total_dom_leaf_area
h_pp <- ggplot(aes(y=dom_shannon, x=total_dom_leaf_area, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Leaf Area", y="Shannon Index", x="total_dom_leaf_area (scaled)") + geom_smooth(method = "lm") + theme_project()


#total_dom_leaf_dry_weight
i_pp <- ggplot(aes(y=dom_shannon, x=total_dom_leaf_dry_weight, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Leaf Dry Weight", y="Shannon Index", x="total_dom_leaf_dry_weight (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_totaldom_sla
j_pp <- ggplot(aes(y=dom_shannon, x=av_totaldom_sla, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Avg SLA", y="Shannon Index", x="av_totaldom_sla (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_dom_1_sla
k_pp <- ggplot(aes(y=dom_shannon, x=av_dom_1_sla, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Sp. 1 Avg SLA", y="Shannon Index", x="av_dom_1_sla (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_dom_2_sla
l_pp <- ggplot(aes(y=dom_shannon, x=av_dom_2_sla, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Sp. 2 Avg SLA", y="Shannon Index", x="av_dom_2_sla (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_dom_3_sla
m_pp <- ggplot(aes(y=dom_shannon, x=av_dom_3_sla, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Dom Sp. 3 Avg SLA", y="Shannon Index", x="av_dom_3_sla (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_quad_compaction
n_pp <- ggplot(aes(y=dom_shannon, x=av_quad_compaction, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Avg Quad Comp", y="Shannon Index", x="av_quad_compaction (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_quad_lai
o_pp <- ggplot(aes(y=dom_shannon, x=av_quad_lai, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Avg Quad LAI", y="Shannon Index", x="av_quad_lai (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_quad_gft
p_pp <- ggplot(aes(y=dom_shannon, x=av_quad_gft, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Avg Quad GFT", y="Shannon Index", x="av_quad_gft (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_trans_elevation
q_pp <- ggplot(aes(y=dom_shannon, x=av_trans_elevation, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Avg Trans El", y="Shannon Index", x="av_trans_elevation (scaled)") + geom_smooth(method = "lm") + theme_project()

#av_trans_decomposition
r_pp <- ggplot(aes(y=dom_shannon, x=av_trans_decomposition, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Avg Tran Decomp", y="Shannon Index", x="av_trans_decomposition (scaled)") + geom_smooth(method = "lm") + theme_project()

#min_temp
s_pp <- ggplot(aes(y=dom_shannon, x=min_temp, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Min Temp", y="Shannon Index", x="min_temp (scaled)") + geom_smooth(method = "lm") + theme_project()

#max_temp
t_pp <- ggplot(aes(y=dom_shannon, x=max_temp, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Max Temp", y="Shannon Index", x="max_temp (scaled)") + geom_smooth(method = "lm") + theme_project()

#range_temp
u_pp <- ggplot(aes(y=dom_shannon, x=range_temp, col=site), data=domshannons_rq1.df) + geom_point() + labs(title="S.I. vs Range of Temp", y="Shannon Index", x="range_temp (scaled)") + geom_smooth(method = "lm") + theme_project()


# ggarrange(d_pp, e_pp, f_pp, g_pp, #int dom abundance, overall seedling cover
#           ncol = 2, nrow = 2)
# 
# ggarrange(h_pp, i_pp, j_pp, k_pp,
#           ncol = 2, nrow = 2)
# 
# 
# ggarrange(l_pp, m_pp, n_pp, o_pp, #none 
#           ncol = 2, nrow = 2)
# 
# 
# ggarrange(p_pp, q_pp, r_pp, s_pp, 
#           ncol = 2, nrow = 2)
# 
# ggarrange(t_pp, u_pp)

multiplot(d_pp, g_pp,
          layout = matrix(c(1,2), nrow=1))


}

```

FIGURE #3: (a) Site interaction with sclaed toal dominant abundance against scaled shannon's index. (b) Site interaction with sclaed overal seedling cover against scaled shannon's index.

From this exploration we can see that potentially influential variables are: Total Dominant Abundance, Overall Seedling Cover, Dominant total leaf dry Weight, GFT. As well as the interactions: site:dom_total_abundance and site:overall_seedling_cover.

Important to note: Total Dominant Seedling cover cannot be included as it was used to calculate Shannon's Index. These will now be modelled via GLMM using Baysian INLA. 

#### Correlation

Correlation (of the final predictors investigated) was inspected to ensure there was no interference with the regressions. As seen in the table below, there were no correlations of concern (acceptance level 0.85). 

<!-- TABLE #1: Correlations between overall seedling cover, total dominant leaf dry weight, and average quadrat GFT.  -->
```{r inclide=FALSE}

df <-  subset(domshannons_rq1.df, select = c("overall_seedling_cover", "total_dom_leaf_dry_weight", "av_quad_gft"))

cor(df, use="complete.obs") %>%
  round(digits = 2) %>%
  kable()



```



