---
title: "model_development"
output: html_document
---

A total of 4 models were reviewed, each time assessed on their marginal log-likelihood and inspecting the coefficient's credible intervals. If the credible interval contained 0, the variable was removed and the model was refitted. 

#### Final Model

After elimation, and including site due to the research question, the variables that were suitbale predictors for shannon's index were: overall seedling cover, site:overall seedling cover, total dominant leaf dry weight, and average quadrat GFT. 

<!-- $$Shannon's Index = 0 + {Prinstine} + {Overall Seedling Cover} + {SiteP:Overall Seedling Cover} + {Total Dominant Leaf Dry Weight} + {Average Quadrat GFT} + {transect} + {residual}$$ -->

The Marginal log-Likelihood was -24.15 (compared to -42.55, from the initial model). 

```{r}

formula_fit4_int = dom_shannon ~ site + overall_seedling_cover + 
                              site:overall_seedling_cover  + total_dom_leaf_dry_weight + av_quad_gft + 
                               f(site_trans, model="iid") 

result_fit4_int <- inla(formula_fit4_int, family="gaussian", 
                        data=domshannons_rq1.df,
                       control.compute =list(dic=TRUE, waic= TRUE, cpo = TRUE, mlik = TRUE,config=TRUE),
                       control.predictor=list(compute=T))

# summary(result_fit4_int)
# Marginal log-Likelihood:  -24.15
```


#### Model Fit
The residual plot in the figure below appears to have an even spread of positive and negative values in the middle range of fitted values. So there are no concerns for model fit, while also considering the small sample size of 30 observations. 


```{r, fig.width = 5}
# summary(fit)
fit <- result_fit4_int
predictions <- fit$summary.fitted.values$mean
dataset <- domshannons_rq1.df

dataset$fitted <- predictions
dataset$observed <- dataset$dom_shannon

pred.df <- dataset %>% 
  ungroup() %>%
      mutate(residuals = observed - fitted,
             std_residuals = (residuals - mean(residuals))/sqrt(var(residuals)),
             cpo = fit$cpo$pit)

## Fitted vs Predicted
fit_vs_pred <- pred.df %>%
  ggplot(aes(x = observed, y = fitted)) +
  geom_point() +
  xlab("Observed Mean SLA (CA)") +
  ylab("Fitted Values") +
  theme_project() +
  coord_equal() +
  geom_abline() +
  ggtitle("Observed vs Fitted SLA")

## Fitted vs Standardised Residuals
fit_vs_res <- pred.df %>%
  ggplot(aes(x = fitted, y = std_residuals)) +
  geom_point() +
  xlab("Fitted Values") +
  ylab("Standardised Residuals") +
  theme_project() +
  geom_abline(slope = 0)+
  geom_abline(slope = 0, intercept = 1.5)+
  geom_abline(slope = 0, intercept = -1.5) +
  ggtitle("Standardised Residuals")

multiplot(fit_vs_pred, fit_vs_res,
          layout = matrix(c(1,2), nrow = 1))


 # Histogram of predictions
hist_res <- pred.df %>%
  ggplot(aes(x = fitted)) +
  geom_histogram(bins=7) +
  theme_project() +
  ggtitle("Histograms of Fitted Values")
  

# CPO Values: QQ plot and Histogram
hist_cpo <- pred.df %>%
  ggplot(aes(x = cpo)) +
  geom_histogram(bins=7) +
  theme_project() +
  ggtitle("Histograms of CPO")
```


Both QQ plots for the residuals and CPO values in the figure below are beleived to be acceptable as they do show to deviate at the tails and the residaul Q-Q plot demonstrate a reasonable fit for the middel values. There is a little concern in the QQ for the middle values. This is represented in the histograms on the right side, but no major deviations are noticeable so this model is still beleived to have the best fit.  

```{r, fig.height = 5, fig.width = 7}
par(mfrow = c(2,2))
# CPI QQ plot
qqnorm(pred.df$cpo)
qqline(pred.df$cpo)
title("CPO                                         ")

CPO <- pred.df$cpo
hist(CPO)

# Residuals QQ plot
qqnorm(pred.df$residuals)
qqline(pred.df$residuals)
title("Residuals                                                   ")

Residuals <- pred.df$residuals
hist(Residuals)

par(mfrow = c(1,1))
```

#### Fixed Effect Credible Intervals

The coefficient plot, in the figure below, outlines the uncertainty in the model as well as showing the credible intervals do not contain 0, meaning they are suitable predictors in this model. For example, for every unit increase in average quadrat GFT (scaled), shannon's index (scaled) increases by 0.002 to 0.1148. Increases also occur with being in the disturbed transects, overall seedling cover and total dominant dry leaf weight. 

```{r, fig.align='center'}

#### Fixed Effect Credible Intervals

## How to look at predictions and compare to original???
{
  
fixed <- summary(fit)$fixed
vec <- fixed[1:length(fixed)]
# random <- summary(fit)$random
n <- length(summary(fit)$fixed)
n1 <- n/7

# Collect and plot the intercals
# How to standardise the intervals?
# Standardise the response variable?
fixed.df <- data.frame(Estimate = row.names(fixed),
Mean = vec[1:n1],
SD = vec[(n1+1):(2*n1)],
quant0.025 = vec[(2*n1+1):(3*n1)],
quant0.5 = vec[(3*n1+1):(4*n1)],
quant0.975 = vec[(4*n1+1):(5*n1)],
mode = vec[(5*n1+1):(6*n1)]) %>%
mutate(Estimate = factor(Estimate, levels = row.names(fixed)[n1:1], ordered = TRUE)) %>%
tbl_df() %>%
mutate(beta = 0:(n1-1)) %>%
mutate(Est2 = paste0(Estimate, " - b", beta),
Est2 = reorder(Est2, rev(beta)))

fixed.df %>%
ggplot(aes(y = Est2, x = quant0.5, xmin = quant0.025, xmax = quant0.975)) +
geom_errorbarh() +
theme_project() +
ggtitle("Standardised Predictors") +
xlab("Credible Intervals") +
ylab("Parameter") +
geom_vline(xintercept = 0)

}

```

We will look further into the interaction to determine the real fixed effect credible intervals. 


#### Real Fixed Effect Credible Intervals

The figure below shows that overall seedling cover has more than one estimate when moving from disturbed to pristine. Overall seedling cover has no effect in pristine transects, but in disturbed there is a different relationship. This was represented in the interacion preliminary plots.

```{r}

#### Fixed Effect Credible Intervals

## How to look at predictions and compare to original???
fixed <- summary(fit)$fixed
vec <- fixed[1:length(fixed)]
# random <- summary(fit)$random
n <- length(summary(fit)$fixed)
n1 <- n/7

# Collect and plot the intercals
# How to standardise the intervals?
# Standardise the response variable?
fixed.df <- data.frame(Estimate = row.names(fixed),
           Mean = vec[1:n1],
           SD = vec[(n1+1):(2*n1)],
           quant0.025 = vec[(2*n1+1):(3*n1)],
           quant0.5 = vec[(3*n1+1):(4*n1)],
           quant0.975 = vec[(4*n1+1):(5*n1)],
           mode = vec[(5*n1+1):(6*n1)]) %>%
  mutate(Estimate = factor(Estimate, levels = row.names(fixed)[n1:1], ordered = TRUE)) %>%
  tbl_df() %>%
  mutate(beta = 0:(n1-1)) %>%
  mutate(Est2 = paste0(Estimate, " - b", beta),
         Est2 = reorder(Est2, rev(beta)))

# fixed.df %>%
#   ggplot(aes(y = Est2, x = quant0.5, xmin = quant0.025, xmax = quant0.975)) +
#   geom_errorbarh() +
#   theme_project() +
#   ggtitle("Overall Seedling Cover - Fixed") +
#   xlab("Credible Intervals") +
#   ylab("Parameter") +
#   geom_vline(xintercept = 0)


#### Real Fixed Effect Credible Intervals

# There are three main bits here:
# (1) dataset for median values
# (2) dataset for lower quantile values
# (3) dataset for upper quantile values

# you need to change the numbers below to correspond to your interaction estimates.
# The code will sum up the estimates from the fixed.df dataset above, based on interactions that you specify

# 1intercept
# 2overall_seedlingcover
# 3total_dom_leaf_dry_weight
# 4av_quad_gft
# 5sitep:overallseedlingdover




mean_fixedeffect.df <- data.frame(Parameter = c("Intercept","Overall Seedling Cover")) %>%
  mutate(Disturbed = round(c(sum(fixed.df$quant0.5[c(1)]),
                   sum(fixed.df$quant0.5[c(3)])), digits=1)) %>%
  mutate(Pristine = round(c(sum(fixed.df$quant0.5[c(1, 2)]),
                   sum(fixed.df$quant0.5[c(3, 6)])), digits=1)) %>%
  gather(Scenario, Median, -Parameter)

lb_fixedeffect.df <- data.frame(Parameter = c("Intercept","Overall Seedling Cover")) %>%
  mutate(Disturbed = round(c(sum(fixed.df$quant0.025[c(1)]),
                   sum(fixed.df$quant0.025[c(3)])), digits=1)) %>%
  mutate(Pristine = round(c(sum(fixed.df$quant0.025[c(1, 2)]),
                   sum(fixed.df$quant0.025[c(3, 6)])), digits=1))%>%
  gather(Scenario, LB, -Parameter)

ub_fixedeffect.df <- data.frame(Parameter = c("Intercept","Overall Seedling Cover")) %>%
  mutate(Disturbed = round(c(sum(fixed.df$quant0.975[c(1)]),
                   sum(fixed.df$quant0.975[c(3)])), digits=1)) %>%
  mutate(Pristine = round(c(sum(fixed.df$quant0.975[c(1, 2)]),
                   sum(fixed.df$quant0.975[c(3, 6)])), digits=1)) %>%
  gather(Scenario, UB, -Parameter)


realeffect.df <- lb_fixedeffect.df %>%
  left_join(ub_fixedeffect.df,
            by = c("Parameter", "Scenario")) %>%
  left_join(mean_fixedeffect.df,
            by = c("Parameter", "Scenario"))


realeffect.df %>%
  filter(Parameter == "Overall Seedling Cover") %>%
  select(Scenario, Median, UB, LB, Parameter) %>%
  distinct() %>%
  ggplot(aes(y = Scenario, x = Median, xmin = UB, xmax = LB)) +
  geom_errorbarh() +
  theme_project() +
  ggtitle("Overall Seedling Cover") +
  xlab("Real Effect - Credible Intervals") +
  ylab("Site") +
  geom_vline(xintercept = 0)


```

#### Variation Breakdown

We can see that variation not explained by the fixed effects is mostly explained by the residuals. The figure below clearly outlines that it would appear that the random effects in this model explain very little of the variations, the percentages can be seen in the table below the figure.  

It is important to note that the nested random effect of quadrat in transect is saturated in the model, as there are 30 observations and 30 unique quadrants. Thus this random effect is excluded in the analysis for Shannon's Index. 

<!-- It appears that INLA was unable to accuratly show the variation explained by the random effects.  -->

```{r}

{
## How to look at predictions and compare to original???
random <- summary(fit)$hyperpar
# random

randomeffects <- data.frame(hyperparameter = c("Residual", "Transect"),
precision = random[[1]],
lb = random[[3]],
ub = random[[5]]) %>%
mutate(variance = 1/precision,
varlb = 1/lb,
varub = 1/ub) %>%
mutate(totalvar = sum(variance),
totallb = sum(varlb),
totalub = sum(varub)) %>%
mutate(explained = variance/totalvar,
explainedlb = varlb/totallb,
explainedub = varub/totalub) %>%
arrange(desc(explained))

#
randomeffects %>%
ggplot(aes(y = hyperparameter, x = variance, xmin = varlb, xmax = varub)) +
geom_errorbarh() +
theme_project() +
ggtitle("Hyperparameters") +
xlab("Credible Interval") +
ylab("Hyperparameter")

}

```

```{r}
randomeffects %>%
mutate(`Variation Explained` = percent(explained)) %>%
select(hyperparameter, `Variation Explained`)


```



