---
title: "model_development"
output: html_document
---

```{r}
# This code should be removed when entire process is productionised
dropbox <- "C:\\Users\\Jacob\\Dropbox\\Semester 2 2017\\MXB344\\Project\\Data\\"

load(paste0(dropbox, "sla_com.RData"))

sladata <- sla_com.df

response_variables <- c("sla_cw_mean", "sla_cw_sd")
```

  * leaf area - photosynthetic aparatus of the plant
  * amount of investment of dry matter (plant investment into growth defence trade off) -> Most dominant species most compettitive, higher specific leaf area
  * community aggregated sla provides insight to how plants function as a quadrat
    * high community aggregated sla -> infer plants in that plot growing faster
    * low sla -> plasticity to disturbance

The following subsections investigate key relationships that explain the mean and variance of community aggregated SLA.
    
### SLA vs Site
```{r}
# Mean sla plot
sladata %>%
  ggplot(aes(x = site, y = sla_cw_mean, col = site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Site")+
  xlab("Site") +
  ylab("Mean SLA (CW)") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_mean)))

# variance sla plot
sladata %>%
  ggplot(aes(x=site, y = sla_cw_sd^2, col = site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site")  +
  ggtitle("Variance of Community Aggregated SLA vs Site")+
  xlab("Site") +
  ylab("Variance of SLA (CW)")  +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_sd)^2))

```

### Overall Seedling Cover
```{r}
# Mean sla plot
sladata %>%
  ggplot(aes(x = overall_seedling_cover, y = sla_cw_mean)) +
  geom_point() +
  theme_project() +
  # scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Cover")+
  xlab("Overall Seedling Cover") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_mean)))

# variance sla plot
sladata %>%
  ggplot(aes(x = overall_seedling_cover, y = sla_cw_sd^2)) +
  geom_point() +
  theme_project() +
  # scale_colour_manual(values = colours.site, name = "Site")  +
  ggtitle("Variance of Community Aggregated SLA vs Cover")+
  xlab("Overall Seedling Cover") +
  ylab("Variance of SLA (CW)") +
  geom_smooth(method = "lm")  +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_sd)^2))

```

### Total Dominant Species Abundance
```{r}
# Mean sla plot
sladata %>%
  ggplot(aes(x = total_dom_abundance, y = sla_cw_mean, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Abundance")+
  xlab("Total Dominant Species Abundance") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_mean)))

# variance sla plot
sladata %>%
  ggplot(aes(x = total_dom_abundance, y = sla_cw_sd^2, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site")  +
  ggtitle("Variance of Community Aggregated SLA vs Abundance")+
  xlab("Total Dominant Species Abundance") +
  ylab("Variance of SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_sd)^2))
```

### Compaction
```{r}
# Mean sla plot
sladata %>%
  ggplot(aes(x = av_quad_compaction, y = sla_cw_mean, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Compaction")+
  xlab("Compaction (pressure)") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_mean)))

# variance sla plot
sladata %>%
  ggplot(aes(x = av_quad_compaction, y = sla_cw_sd^2, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site")  +
  ggtitle("Variance of Community Aggregated SLA vs Compaction")+
  xlab("Compaction (pressure)") +
  ylab("Variance of SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_sd)^2))
```

### Leaf Area Index
```{r}
sladata %>%
  ggplot(aes(x=av_quad_lai, y=av_quad_gft)) +
  geom_point()

sladata %>%
  select(av_quad_lai, av_quad_gft) %>%
  cor()
```

```{r}
# Mean sla plot
sladata %>%
  ggplot(aes(x = av_quad_lai, y = sla_cw_mean, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Compaction")+
  xlab("Leaf Area Index") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_mean)))

# variance sla plot
sladata %>%
  ggplot(aes(x = av_quad_lai, y = sla_cw_sd^2, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site")  +
  ggtitle("Variance of Community Aggregated SLA vs Compaction")+
  xlab("Leaf Area Index") +
  ylab("Variance of SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_sd)^2))
```

### Gap Fraction Threshold
```{r}
sladata %>%
  ggplot(aes(x=av_quad_lai, y=av_quad_gft)) +
  geom_point()

sladata %>%
  select(av_quad_lai, av_quad_gft) %>%
  cor()
```

```{r}
# Mean sla plot
sladata %>%
  ggplot(aes(x = av_quad_gft, y = sla_cw_mean, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Compaction")+
  xlab("Gap Fraction Threshold") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_mean)))

# variance sla plot
sladata %>%
  ggplot(aes(x = av_quad_gft, y = sla_cw_sd^2, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site")  +
  ggtitle("Variance of Community Aggregated SLA vs Compaction")+
  xlab("Gap Fraction Threshold") +
  ylab("Variance of SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_sd)^2))
```

### Decomposition
```{r}
# Mean sla plot
sladata %>%
  ggplot(aes(x = av_trans_decomposition, y = sla_cw_mean, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Compaction")+
  xlab("Decomposition (grams/days)") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_mean)))

# variance sla plot
sladata %>%
  ggplot(aes(x = av_trans_decomposition, y = sla_cw_sd^2, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site")  +
  ggtitle("Variance of Community Aggregated SLA vs Compaction")+
  xlab("Decomposition (grams/days)") +
  ylab("Variance of SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_sd)^2))
```

### Maximum Temperature
```{r}
# Mean sla plot
sladata %>%
  ggplot(aes(x = max_temp, y = sla_cw_mean, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Compaction")+
  xlab("Maximum Temperature (celsius)") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_mean)))

# variance sla plot
sladata %>%
  ggplot(aes(x = max_temp, y = sla_cw_sd^2, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site")  +
  ggtitle("Variance of Community Aggregated SLA vs Compaction")+
  xlab("Maximum Temperature (celsius)") +
  ylab("Variance of SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw_sd)^2))
```

