---
title: "model_development"
output: html_document
---

```{r}
# This code should be removed when entire process is productionised
load(paste0(data_folder, "sla_com.RData"))

response_variables <- c("sla_ca_mean", "sla_ca_sd")
```

  <!-- * leaf area - photosynthetic aparatus of the plant -->
  <!-- * amount of investment of dry matter (plant investment into growth defence trade off) -> Most dominant species most compettitive, higher specific leaf area -->
  <!-- * community aggregated sla provides insight to how plants function as a quadrat -->
  <!--   * high community aggregated sla -> infer plants in that plot growing faster -->
  <!--   * low sla -> plasticity to disturbance -->

### Random Effects
The figure below shows the variation in community aggregated sla between different transects. This demonstrates that some variation can be attributed to the different transects in the rainforest.

```{r}
trans <- sla_com.df %>%
  ggplot(aes(x = site_trans, y = sla_ca_mean, col = site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("SLA (CA) vs Site") +
  xlab("Transect") +
  ylab("SLA (CA)") +
  scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_mean)))

quad <- sla_com.df %>%
  ggplot(aes(x = paste0(site_trans, quadrat), y = sla_ca_mean, col = site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("SLA (CA) vs Site") +
  xlab("Quadrat:Transect") +
  ylab("SLA (CA)") +
  scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_mean)))

multiplot(trans, #quad,
          layout = matrix(c(1,2), nrow = 1))
```
    
### Site
The figure below demonstrates the difference between community aggregated SLA between different areas of the rainforest. We see that there is a distinct increase in the SLA of communities in pristine rainforests. There also appears to be a larger spread for pristine communities. The log of SLA is shown on the right side of the figure.

```{r}
var <- "site"
# ggsave(paste0(data_folder, "sla_", var,"_mean.png"), width = 5, height = 6, dpi = 500)
# ggsave(paste0(data_folder, "sla_", var,"_var.png"), width = 5, height = 6, dpi = 500)

# Mean sla plot
sla_norm <- sla_com.df %>%
  ggplot(aes(x = site, y = sla_ca_mean, col = site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("SLA (CA) vs Site") +
  xlab("Site") +
  ylab("SLA (CA)") +
  scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_mean)))

# ggsave(paste0(data_folder, "sla_", var,"_mean.png"), width = 3.5, height = 3.5, dpi = 900)

sla_log <- sla_com.df %>%
  ggplot(aes(x = site, y = log(sla_ca_mean), col = site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Log SLA (CA) vs Site") +
  xlab("Site") +
  ylab("Log SLA (CA)") +
  scale_y_continuous(lim = c(0, max(log(sla_com.df$sla_ca_mean))))


multiplot(sla_norm, sla_log,
          layout = matrix(c(1,2), nrow = 1))

# variance sla plot
# sla_com.df %>%
#   ggplot(aes(x=site, y = sla_ca_sd^2, col = site)) +
#   geom_boxplot() +
#   theme_project() +
#   scale_colour_manual(values = colours.site, name = "Site")  +
#   ggtitle("Variance of SLA vs Site")+
#   xlab("Site") +
#   ylab("Variance of SLA (CA)")  +
#   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_sd)^2))

# ggsave(paste0(data_folder, "sla_", var,"_var.png"), width = 3.5, height = 3.5, dpi = 900)
```

Other variables such as overall seedling cover and abundance showed positive relationships with community aggegated sla.

### Overall Seedling Cover

As expected, the figure below shows the value of community weighted SLA increases as the overall seedling cover increases. There is a slight ihint of an interaction between overall seedling cover and site, so this will be further investigated in the model.

```{r}
# Mean sla plot
sla_com.df %>%
  ggplot(aes(x = overall_seedling_cover, y = sla_ca_mean, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Cover")+
  xlab("Overall Seedling Cover") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_mean)))

# variance sla plot
# sla_com.df %>%
#   ggplot(aes(x = overall_seedling_cover, y = sla_ca_sd^2, col = site)) +
#   geom_point() +
#   theme_project() +
#   scale_colour_manual(values = colours.site, name = "Site")  +
#   ggtitle("Variance of Community Aggregated SLA vs Cover")+
#   xlab("Overall Seedling Cover") +
#   ylab("Variance of SLA (CW)") +
#   geom_smooth(method = "lm")  +
#   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_sd)^2))

```

### Total Dominant Species Abundance
In the figure below, as the total abundance increases, we observe that community aggregated SLA also increases. There is more evidence here suggesting an interation between abundance and site. 

```{r}
# Mean sla plot
sla_com.df %>%
  ggplot(aes(x = total_dom_abundance, y = sla_ca_mean, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Abundance")+
  xlab("Total Dominant Species Abundance") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_mean)))

# variance sla plot
# sla_com.df %>%
#   ggplot(aes(x = total_dom_abundance, y = sla_ca_sd^2, col = site)) +
#   geom_point() +
#   theme_project() +
#   scale_colour_manual(values = colours.site, name = "Site")  +
#   ggtitle("Variance of Community Aggregated SLA vs Abundance")+
#   xlab("Total Dominant Species Abundance") +
#   ylab("Variance of SLA (CW)") +
#   geom_smooth(method = "lm") +
#   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_sd)^2))
```


No other predictor variables presented any meaningful relationship with community aggregated SLA, so are not reported here.

### Correlation
From the table below, we observe the correlation between overall cover and total abundance. There is no evidence of a high correlation, so both variables are included in model development.

```{r}
sla_com.df %>%
  select(overall_seedling_cover, total_dom_abundance) %>%
  cor() %>%
  round(digits = 2) %>%
  kable(caption = "SLA Aggregated Model: Predictor Correlation")


```

<!-- ### Compaction -->
<!-- ```{r} -->
<!-- # Mean sla plot -->
<!-- sla_com.df %>% -->
<!--   ggplot(aes(x = av_quad_compaction, y = sla_ca_mean, col = site)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site, name = "Site") + -->
<!--   ggtitle("Mean Community Aggregated SLA vs Compaction")+ -->
<!--   xlab("Compaction (pressure)") + -->
<!--   ylab("Mean SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_mean))) -->

<!-- # variance sla plot -->
<!-- sla_com.df %>% -->
<!--   ggplot(aes(x = av_quad_compaction, y = sla_ca_sd^2, col = site)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site, name = "Site")  + -->
<!--   ggtitle("Variance of Community Aggregated SLA vs Compaction")+ -->
<!--   xlab("Compaction (pressure)") + -->
<!--   ylab("Variance of SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_sd)^2)) -->
<!-- ``` -->

<!-- ### Leaf Area Index -->
<!-- ```{r} -->
<!-- sla_com.df %>% -->
<!--   ggplot(aes(x=av_quad_lai, y=av_quad_gft)) + -->
<!--   geom_point() -->

<!-- sla_com.df %>% -->
<!--   select(av_quad_lai, av_quad_gft) %>% -->
<!--   cor() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Mean sla plot -->
<!-- sla_com.df %>% -->
<!--   ggplot(aes(x = av_quad_lai, y = sla_ca_mean, col = site)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site, name = "Site") + -->
<!--   ggtitle("Mean Community Aggregated SLA vs Compaction")+ -->
<!--   xlab("Leaf Area Index") + -->
<!--   ylab("Mean SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_mean))) -->

<!-- # variance sla plot -->
<!-- sla_com.df %>% -->
<!--   ggplot(aes(x = av_quad_lai, y = sla_ca_sd^2, col = site)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site, name = "Site")  + -->
<!--   ggtitle("Variance of Community Aggregated SLA vs Compaction")+ -->
<!--   xlab("Leaf Area Index") + -->
<!--   ylab("Variance of SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_sd)^2)) -->
<!-- ``` -->

<!-- ### Gap Fraction Threshold -->
<!-- ```{r} -->
<!-- sla_com.df %>% -->
<!--   ggplot(aes(x=av_quad_lai, y=av_quad_gft)) + -->
<!--   geom_point() -->

<!-- sla_com.df %>% -->
<!--   select(av_quad_lai, av_quad_gft) %>% -->
<!--   cor() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Mean sla plot -->
<!-- sla_com.df %>% -->
<!--   ggplot(aes(x = av_quad_gft, y = sla_ca_mean, col = site)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site, name = "Site") + -->
<!--   ggtitle("Mean Community Aggregated SLA vs GFT")+ -->
<!--   xlab("Gap Fraction Threshold") + -->
<!--   ylab("Mean SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_mean))) -->

<!-- # variance sla plot -->
<!-- sla_com.df %>% -->
<!--   ggplot(aes(x = av_quad_gft, y = sla_ca_sd^2, col = site)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site, name = "Site")  + -->
<!--   ggtitle("Variance of Community Aggregated SLA vs GFT")+ -->
<!--   xlab("Gap Fraction Threshold") + -->
<!--   ylab("Variance of SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_sd)^2)) -->
<!-- ``` -->

<!-- ### Decomposition -->
<!-- ```{r} -->
<!-- # Mean sla plot -->
<!-- sla_com.df %>% -->
<!--   ggplot(aes(x = av_trans_decomposition, y = sla_ca_mean, col = site)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site, name = "Site") + -->
<!--   ggtitle("Mean SLA vs Decomposition")+ -->
<!--   xlab("Decomposition (grams/days)") + -->
<!--   ylab("Mean SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_mean))) -->



<!-- # variance sla plot -->
<!-- sla_com.df %>% -->
<!--   ggplot(aes(x = av_trans_decomposition, y = sla_ca_sd^2, col = site)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site, name = "Site")  + -->
<!--   ggtitle("Variance SLA vs Decomposition")+ -->
<!--   xlab("Decomposition (grams/days)") + -->
<!--   ylab("Variance of SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_sd)^2)) -->

<!-- ``` -->

<!-- ### Maximum Temperature -->
<!-- ```{r} -->
<!-- # Mean sla plot -->
<!-- sla_com.df %>% -->
<!--   ggplot(aes(x = max_temp, y = sla_ca_mean, col = site)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site, name = "Site") + -->
<!--   ggtitle("Mean Community Aggregated SLA vs Compaction")+ -->
<!--   xlab("Maximum Temperature (celsius)") + -->
<!--   ylab("Mean SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_mean))) -->

<!-- # variance sla plot -->
<!-- sla_com.df %>% -->
<!--   ggplot(aes(x = max_temp, y = sla_ca_sd^2, col = site)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site, name = "Site")  + -->
<!--   ggtitle("Variance of Community Aggregated SLA vs Compaction")+ -->
<!--   xlab("Maximum Temperature (celsius)") + -->
<!--   ylab("Variance of SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sla_com.df$sla_ca_sd)^2)) -->
<!-- ``` -->

