---
title: "model_development"
output: html_document
---

```{r}
# This code should be removed when entire process is productionised
load(paste0(data_folder, "sla_ind.RData"))

sladata <- sla_ind.df

response_variables <- c("sla_cw", "sla_cw_sd")
```

### Random Effects
```{r}
sladata %>%
  ggplot(aes(x = transect, y = log(sla_cw))) +
  geom_boxplot() +
  ggtitle("Transect Difference")+
  theme_project()

sladata %>%
  ggplot(aes(x = paste0("T", transect, ":Q", quadrat), y = log(sla_cw))) +
  geom_boxplot() +
  ggtitle("Quadrat:Transect Difference")+
  theme_project()
      


```

```{r}
sladata %>%
  group_by(site_trans) %>%
  summarise(mean_log_sla_cw = mean(log(sla_cw))) %>%
  mutate(variation = var(mean_log_sla_cw))
  


sladata %>%
  ggplot(aes(x = site_trans, y = log(sla_cw))) +
  geom_boxplot() +
  ggtitle("Site:Transect Difference") +
  theme_project()

sladata %>%
  ggplot(aes(x = paste0(site, transect, quadrat), y = log(sla_cw))) +
  geom_boxplot() +
  ggtitle("Site:Transect:Qudrat Difference") +
  theme_project()

```

  * leaf area - photosynthetic aparatus of the plant
  * amount of investment of dry matter (plant investment into growth defence trade off) -> Most dominant species most compettitive, higher specific leaf area
  * community aggregated sla provides insight to how plants function as a quadrat
    * high community aggregated sla -> infer plants in that plot growing faster
    * low sla -> plasticity to disturbance

The following subsections investigate key relationships that explain the mean and variance of community aggregated SLA.
    
### SLA vs Site
```{r}
var <- "domspecies"
# ggsave(paste0(data_folder, "sla_", var,"_mean.png"), width = 5, height = 6, dpi = 500)
# ggsave(paste0(data_folder, "sla_", var,"_var.png"), width = 5, height = 6, dpi = 500)

# Mean sla plot
sladata %>%
  ggplot(aes(x = site, y = sla_cw, col = site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("SLA vs Dominant Species ID") +
  xlab("Site") +
  ylab("SLA (CW)") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw))) +
  facet_wrap("dom_species_id", scale = "free_y")

ggsave(paste0(data_folder, "scale_sla_cw_", var,"_mean.png"), width = 4, height = 3.5, dpi = 900)

sladata %>%
  ggplot(aes(x = site, y = sla_cw, col = site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("(Unscaled) SLA vs Site") +
  xlab("Site") +
  ylab("SLA (CW)") +
  # scale_y_continuous(lim = c(0, max(sladata$sla_cw))) +
  facet_wrap("dom_species_id", scale = "free_y")

ggsave(paste0(data_folder, "unscale_sla_cw_", var,"_mean.png"), width = 4, height = 3.5, dpi = 900)

```

### Overall Seedling Cover
```{r}
# Meansla plot
sladata %>%
  ggplot(aes(x = overall_seedling_cover, y = sla_cw, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Cover")+
  xlab("Overall Seedling Cover") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw)))
```

<!-- ### Total Dominant Species Abundance -->
<!-- ```{r} -->
<!-- # Mean sla plot -->
<!-- sladata %>% -->
<!--   ggplot(aes(x = total_dom_abundance, y = sla_cw, col = site)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site, name = "Site") + -->
<!--   ggtitle("Mean Community Aggregated SLA vs Abundance")+ -->
<!--   xlab("Total Dominant Species Abundance") + -->
<!--   ylab("Mean SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sladata$sla_cw))) -->
<!-- ``` -->

### Compaction
```{r}
# Mean sla plot
sladata %>%
  ggplot(aes(x = av_quad_compaction, y = sla_cw, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Compaction")+
  xlab("Compaction (pressure)") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw)))
```

### Leaf Area Index
```{r}
sladata %>%
  ggplot(aes(x=av_quad_lai, y=av_quad_gft)) +
  geom_point()

sladata %>%
  select(av_quad_lai, av_quad_gft) %>%
  cor()
```

```{r}
# Mean sla plot
sladata %>%
  filter(av_quad_lai != disturbed_mean_lai) %>%
  ggplot(aes(x = (av_quad_lai), y = log(sla_cw), col = dom_species_id)) +
  geom_point(size = 0.9) +
  theme_project() +
  # scale_colour_manual(values = colours.site, name = "Site") +
  scale_colour_tableau(name = "Dom Species ID") +
  ggtitle("SLA vs LAI (No Impute)")+
  xlab("Leaf Area Index") +
  ylab("SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(log(sladata$sla_cw))))


ggsave(paste0(data_folder, "scale_sla_cw_", "LAI","_mean.png"), width = 4, height = 3.5, dpi = 900)

```

### Gap Fraction Threshold
```{r}
sladata %>%
  ggplot(aes(x=av_quad_lai, y=av_quad_gft)) +
  geom_point()

sladata %>%
  select(av_quad_lai, av_quad_gft) %>%
  cor()
```

```{r}
# Mean sla plot
sladata %>%
  ggplot(aes(x = av_quad_gft, y = sla_cw, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Compaction")+
  xlab("Gap Fraction Threshold") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw)))

```

### Decomposition
```{r}
# Mean sla plot
sladata %>%
  ggplot(aes(x = av_trans_decomposition, y = sla_cw, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Compaction")+
  xlab("Decomposition (grams/days)") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw)))

```

### Maximum Temperature
```{r}
# Mean sla plot
sladata %>%
  ggplot(aes(x = max_temp, y = sla_cw, col = site)) +
  geom_point() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Mean Community Aggregated SLA vs Compaction")+
  xlab("Maximum Temperature (celsius)") +
  ylab("Mean SLA (CW)") +
  geom_smooth(method = "lm") +
  scale_y_continuous(lim = c(0, max(sladata$sla_cw)))

```

