---
title: "model_development"
output: html_document
---

```{r}
# This code should be removed when entire process is productionised
load(paste0(data_folder, "sla_ind.RData"))

sla_ind.df <- sla_ind.df

response_variables <- c("sla_cw", "sla_cw_sd")
```

##### Random Effects
The figure below demonstrates the variation between transects and quadrats nested in transects. There is a slight difference between transect, and a large amount of variation observed between quadrats.

```{r}
trans2 <- sla_ind.df %>%
  ggplot(aes(x = site_trans, y = log(sla_cw))) +
  geom_boxplot() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Log SLA Transect Variation") +
  xlab("Transect") +
  ylab("Log SLA (CW)")

quad2 <- sla_ind.df %>%
  ggplot(aes(x = paste0(site_trans, ":Q", quadrat), y = log(sla_cw))) +
  geom_boxplot() +
  ggtitle("Log SLA Nested Quadrat Variation")+
  theme_project() +
  xlab("Quadrat") +
  ylab("Log SLA (CW)") +
  scale_x_discrete(labels = NULL)
      
multiplot(trans2, quad2,
          layout = matrix(c(1,2), nrow = 2))

```

##### Species and Site
The figure below highlights the weighted SLA differences between species, and the interaction with disturbance. Dominant species 1 has a higher SLA in pristine areas of the rainforest. Where as dominant species 3 appears to decrease in SLA when in pristine forest areas, however there is a large overlap between sites. Dominant species 2 doesn't have any significant change between sites. This suggests an interaction term will be significant.

```{r}
var <- "domspecies"
# ggsave(paste0(data_folder, "sla_", var,"_mean.png"), width = 5, height = 6, dpi = 500)
# ggsave(paste0(data_folder, "sla_", var,"_var.png"), width = 5, height = 6, dpi = 500)

# Mean sla plot
scaled <- sla_ind.df %>%
  ggplot(aes(x = site, y = log(sla_cw), col = site)) +
  geom_boxplot() +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site") +
  ggtitle("Log SLA (CW) vs Species") +
  xlab("Site") +
  ylab("Log SLA (CW)") +
  # scale_y_continuous(lim = c(0, max(sla_ind.df$sla_cw))) +
  facet_wrap("dom_species_id")

# ggsave(paste0(data_folder, "scale_sla_cw_", var,"_mean.png"), width = 4, height = 3.5, dpi = 900)

# unscaled <- sla_ind.df %>%
#   ggplot(aes(x = site, y = log(sla_cw), col = site)) +
#   geom_boxplot() +
#   theme_project() +
#   scale_colour_manual(values = colours.site, name = "Site") +
#   ggtitle("(Unscaled) SLA vs Species") +
#   xlab("Site") +
#   ylab("SLA (CW)") +
#   # scale_y_continuous(lim = c(0, max(sla_ind.df$sla_cw))) +
#   facet_wrap("dom_species_id", scale = "free_y")

# ggsave(paste0(data_folder, "unscale_sla_cw_", var,"_mean.png"), width = 4, height = 3.5, dpi = 900)

# multiplot(scaled, unscaled,
#           layout = matrix(c(1,2), nrow = 1))

scaled 
```

##### Overall Seedling Cover
In the figure below, we observe the relationship between overall seedling cover and the log of weighted SLA. This variables appears to have a significant effect on species ID 1, however this is influenced by the low seedling cover of a single quadrat. An interaction term will be investigated to see if the overall model improves.

```{r}
# Meansla plot
sla_ind.df %>%
  ggplot(aes(x = overall_seedling_cover, y = log(sla_cw), col = dom_species_id)) +
  geom_point() +
  theme_project() +
  # scale_colour_manual(values = colours.site, name = "Site") +
  scale_colour_tableau(name = "Dom Species ID")+
  ggtitle("Log SLA (CW) vs Cover")+
  xlab("Overall Seedling Cover") +
  ylab("Log SLA (CW)") +
  geom_smooth(method = "lm")
```

<!-- ### Total Dominant Species Abundance -->
<!-- ```{r} -->
<!-- # Mean sla plot -->
<!-- sla_ind.df %>% -->
<!--   ggplot(aes(x = total_dom_abundance, y = sla_cw, col = site)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   scale_colour_manual(values = colours.site, name = "Site") + -->
<!--   ggtitle("Mean Community Aggregated SLA vs Abundance")+ -->
<!--   xlab("Total Dominant Species Abundance") + -->
<!--   ylab("Mean SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sla_ind.df$sla_cw))) -->
<!-- ``` -->

<!-- ##### Compaction -->
<!-- ```{r} -->
<!-- # Mean sla plot -->
<!-- sla_ind.df %>% -->
<!--   ggplot(aes(x = av_quad_compaction, y = sla_cw, col = dom_species_id)) + -->
<!--   geom_point() + -->
<!--   theme_project() + -->
<!--   # scale_colour_manual(values = colours.site, name = "Site") + -->
<!--   scale_colour_tableau(name = "Dominant Species ID") + -->
<!--   ggtitle("Mean Community Aggregated SLA vs Compaction")+ -->
<!--   xlab("Compaction (pressure)") + -->
<!--   ylab("Mean SLA (CW)") + -->
<!--   geom_smooth(method = "lm") + -->
<!--   scale_y_continuous(lim = c(0, max(sla_ind.df$sla_cw))) -->
<!-- ``` -->

##### Leaf Area Index
The figure below demonstrates the relationship between LAI and log weighted SLA. As observed, the increase in LAI has a different effect depending on the species. Dominant species 2 is the odd one out with a negative relationship with LAI. This will be investigated as an interaction relationship in the model.

```{r}
# Mean sla plot
sla_ind.df %>%
  filter(av_quad_lai != disturbed_mean_lai) %>%
  ggplot(aes(x = (av_quad_lai), y = log(sla_cw), col = dom_species_id)) +
  geom_point() +
  theme_project() +
  # scale_colour_manual(values = colours.site, name = "Site") +
  scale_colour_tableau(name = "Dom Species ID") +
  ggtitle("Log SLA vs LAI (No Impute)")+
  xlab("Leaf Area Index") +
  ylab("Log SLA (CW)") +
  geom_smooth(method = "lm")


# ggsave(paste0(data_folder, "scale_sla_cw_", "LAI","_mean.png"), width = 4, height = 3.5, dpi = 900)

```


##### Correlation
All other exploratory graphs are not included in this report, due to no meaningful relationship observed or a high correlation (correlation between LAI and GFT ~ 0.8). The table below demonstrates the low correlation of the main predictors.

```{r}
sla_ind.df %>%
  select(av_quad_lai, overall_seedling_cover) %>%
  cor() %>%
  round(digits = 2) %>%
  kable(caption = "SLA Weighted Model: Predictor Correlation")
```

