---
title: "model_development"
output: html_document
---

```{r}
load(paste0(data_folder, "sla_ind.RData"))
```

```{r}
# define the vector of possible predictors, exclude random effects
response <- "sla_cw"
temp_predictors <- names(sla_ind.df)[-(which(names(sla_ind.df) %in% c("transect", "quadrat", "site", "dom_species_id", "sla_cw", "dom_seedling_cover", "overall_seedling_cover",
"dom_abundance", "scaled_dom_seedling_cover", "scaled_overall_seedling_cover",
"scaled_dom_abundance", "dom_sla", "min_temp", "range_temp")))]

# Remove all leaf data
# interactions <- c("site:dom_species_id", "site:av_quad_gft", "site:av_quad_compaction",
#          "dom_species_id:scaled_av_trans_elevation", "dom_species_id:av_quad_gft", "dom_species_id:av_quad_compaction")

predictors <- c(temp_predictors, paste0(temp_predictors, "+", temp_predictors, ":site"), paste0(temp_predictors, "+", temp_predictors, ":dom_species_id"))
# predictors <- c(temp_predictors, interactions)

# Iterate through code that creates all possible combinations of predictors: 7 predictors means 7^2 combinations
possible_predictor_combinations <- list()
index <- 1

for (i in 1:length(predictors)) {
  for (j in i:length(predictors)) {
  possible_predictor_combinations[[index]] <- i:j
  index <- index + 1
  }
}

# Create formula's
formula_string_combinations <- list()

for (i in 1:length(possible_predictor_combinations)) {

  formula_string_combinations[[i]] <- predictors[possible_predictor_combinations[[i]][1]]

  if (length(possible_predictor_combinations[[i]]) > 1) {
    for (j in 2:length(possible_predictor_combinations[[i]])) {
      formula_string_combinations[[i]] <- paste(formula_string_combinations[[i]],
                                                predictors[possible_predictor_combinations[[i]][j]],
                                                sep = " + ")
    }
  }

}

# Find the full formula of predictors for INLA step
length_formulastring <- data.frame(Index=NA, Length=NA)

for (i in 1:length(formula_string_combinations)) {
  length_formulastring[i,1] <- i
  length_formulastring[i,2] <- nchar(formula_string_combinations[[i]])
}

full_formula <- length_formulastring %>% 
  arrange(desc(Length)) %>%
  head(1) %>%
  select(Length) %>%
  unlist(use.names = FALSE)
```




<!-- ####  Stepwise for Weighted -->
<!-- ```{r} -->
<!-- # Run all possible INLA models -->
<!-- loglinear_stepwise_summary_w <- data.frame(Formula = "-", Log_Likelihood = NA) -->

<!-- # In for loop, run the model and combine the log likelihood estimate into a data.frame -->
<!-- for (i in 1:length(formula_string_combinations)) { -->
<!-- inla_formula <- as.formula(paste0("log(sla_cw) ~ site + dom_species_id + site:dom_species_id + ", -->
<!--                           formula_string_combinations[[i]], -->
<!--                           " + f(transect, model='iid') + f(quadrat:transect, model = 'iid')")) -->

<!-- fit <- inla(inla_formula, -->
<!--             family = "gaussian", -->
<!--             data = sla_ind.df) -->

<!-- loglinear_stepwise_summary_w <- loglinear_stepwise_summary_w %>% -->
<!--   rbind(data.frame(Formula = formula_string_combinations[[i]], -->
<!--                    Log_Likelihood = summary(fit)[["mlik"]][2])) -->
<!-- print(i) -->
<!-- } -->

<!-- save(loglinear_stepwise_summary_w, file = paste0(data_folder, "loglinear_stepwise_summary_w.RData")) -->

<!-- # load(paste0(dropbox, "loglinear_stepwise_summary.RData")) -->
<!-- #  -->
<!-- # top10 <- loglinear_stepwise_summary %>% -->
<!-- #   arrange(desc(Log_Likelihood)) %>% -->
<!-- #   head(10) -->
<!-- #  -->
<!-- # top10 -->
<!-- ``` -->

<!-- ```{r} -->

<!-- load(paste0(data_folder, "loglinear_stepwise_summary_w.RData")) -->

<!-- loglinear_stepwise_summary_w %>% -->
<!--   arrange(desc(Log_Likelihood)) %>% -->
<!--   head(5) -->


<!-- ``` -->




#### Final Model
The final model regressed the log of community weighted SLA by site, species ID and LAI, with interactions terms with the species ID. This model includes quadrats nested in transect as a random effect due to the large number of replicates. 

<!-- \[ -->
<!-- log(SLA_{Community Aggregated}) = \beta_0 + \beta_{Pristine} + \beta_{Species ID 2} + \beta_{Species ID 3}  + \beta_{LAI} + \beta_{Overall Seedling Cover} + \beta_{Pristine:Species ID 2} + \beta_{Pristine:Species ID 3}  + \beta_{Species ID 2:LAI} + \beta_{Species ID 3:LAI}  + \varepsilon_{transect} + \varepsilon_{quadrat:transect} + \varepsilon_{residual} -->
<!-- \] -->


<!-- ##### Bayesian -->

```{r}
sla_ind.df %<>% 
  mutate(sq_av_quad_lai = av_quad_lai^2) %>%
  mutate(scaled_sq_av_quad_lai = (sq_av_quad_lai - mean(sq_av_quad_lai))/sqrt(var(sq_av_quad_lai)))

# RUn a model on the top 3 variables identified
inla_formula <- log(sla_cw) ~  site + dom_species_id + site:dom_species_id + scaled_av_quad_lai +  scaled_av_quad_lai:dom_species_id + scaled_overall_seedling_cover + scaled_overall_seedling_cover:dom_species_id + f(site_trans, model="iid") + f(quadrat:site_trans, model = "iid")


# inla_formula <- 

fit <- inla(inla_formula,
            family = "gaussian",
            data = sla_ind.df,
            control.compute =list(dic=TRUE, waic= TRUE, cpo = TRUE, 
                                  mlik = TRUE,config=TRUE),
            control.predictor=list(compute=T))


# analyse the output of the model
# summary(fit)
```



#### Model Fit
The figure below compares the fitted predictions against the observed weighted SLA values. No observeable patterns can be determined between either graph, suggesting the model is appropriate. There are some standardised residuals that deviate more than 1.5 standard deviations from the zero line for the lower fitted values. However, this does not raise any concerns for model fit.

```{r, fig.width = 5}
# summary(fit)
predictions <- fit$summary.fitted.values$mean
dataset <- sla_ind.df

pred.df <- dataset %>% 
      mutate(fitted = predictions,
             observed = log(sla_cw),
             residuals = observed - fitted,
             std_residuals = (residuals - mean(residuals))/sqrt(var(residuals)),
             cpo = fit$cpo$pit)

## Fitted vs Predicted
fit_vs_pred <- pred.df %>%
  ggplot(aes(x = observed, y = fitted)) +
  geom_point() +
  xlab("Observed Mean SLA (CA)") +
  ylab("Fitted Values") +
  theme_project() +
  coord_equal() +
  geom_abline() +
  ggtitle("Observed vs Fitted SLA")

## Fitted vs Standardised Residuals
fit_vs_res <- pred.df %>%
  ggplot(aes(x = fitted, y = std_residuals)) +
  geom_point() +
  xlab("Fitted Values") +
  ylab("Standardised Residuals") +
  theme_project() +
  geom_abline(slope = 0)+
  geom_abline(slope = 0, intercept = 1.5)+
  geom_abline(slope = 0, intercept = -1.5) +
  ggtitle("Standardised Residuals")

multiplot(fit_vs_pred, fit_vs_res,
          layout = matrix(c(1,2), nrow = 1))


 # Histogram of predictions
hist_res <- pred.df %>%
  ggplot(aes(x = fitted)) +
  geom_histogram(bins=7) +
  theme_project() +
  ggtitle("Histograms of Fitted Values")
  

# CPO Values: QQ plot and Histogram
hist_cpo <- pred.df %>%
  ggplot(aes(x = cpo)) +
  geom_histogram(bins=7) +
  theme_project() +
  ggtitle("Histograms of CPO")
```

Observing the QQ plots and histograms in the figure below highlights some interesting trends. The CPO values are closer to the uniform distribution for this model, with evidence from the QQ plot deviateing at the tail ends. The Residual QQ plot deviates more at the lower tail end, resulting in a skewed histogram distribution. However, majority of the residuals align to a normal distribution, so the model is considered appropriate.

```{r, fig.height = 5, fig.width = 7}
par(mfrow = c(2,2))
# CPI QQ plot
qqnorm(pred.df$cpo)
qqline(pred.df$cpo)
title("CPO                                         ")

CPO <- pred.df$cpo
hist(CPO)

# Residuals QQ plot
qqnorm(pred.df$residuals)
qqline(pred.df$residuals)
title("Residuals                                                   ")

Residuals <- pred.df$residuals
hist(Residuals)

par(mfrow = c(1,1))
```





#### Fixed Effect Credible Intervals
A large number of interaction parameters are estimated in this model, as observed in the figure below. The full effect can be determined by combining the interaction effects.

```{r, fig.height = 5}
## How to look at predictions and compare to original???
fixed <- summary(fit)$fixed
vec <- fixed[1:length(fixed)]
# random <- summary(fit)$random
n <- length(summary(fit)$fixed)
n1 <- n/7

# Collect and plot the intercals
# How to standardise the intervals?
# Standardise the response variable?
fixed.df <- data.frame(Estimate = row.names(fixed),
           Mean = vec[1:n1],
           SD = vec[(n1+1):(2*n1)],
           quant0.025 = vec[(2*n1+1):(3*n1)],
           quant0.5 = vec[(3*n1+1):(4*n1)],
           quant0.975 = vec[(4*n1+1):(5*n1)],
           mode = vec[(5*n1+1):(6*n1)]) %>%
  mutate(Estimate = factor(Estimate, levels = row.names(fixed)[n1:1], ordered = TRUE)) %>%
  tbl_df() %>%
  mutate(beta = 0:(n1-1)) %>%
  mutate(Est2 = paste0(Estimate, " - b", beta),
         Est2 = reorder(Est2, rev(beta))) 

fixed.df %>%
  ggplot(aes(y = Est2, x = quant0.5, xmin = quant0.025, xmax = quant0.975)) +
  geom_errorbarh() +
  theme_project() +
  ggtitle("SLA Weighted - Fixed Effects") +
  xlab("Credible Intervals") +
  ylab("Parameter") +
  geom_vline(xintercept = 0)

# ggsave(paste0(data_folder, "scale_sla_cw_", "fixed",".png"), width = 5, height = 3.5, dpi = 900)
```


```{r}
mean_fixedeffect.df <- data.frame(Parameter = c("Intercept","Scaled LAI", "Scaled Overall Seedling Cover")) %>%
  mutate(ID1_D = round(c(sum(fixed.df$quant0.5[c(1)]),
                   sum(fixed.df$quant0.5[c(5)]),
                   sum(fixed.df$quant0.5[c(6)])), digits=4)) %>%
  mutate(ID2_D = round(c(sum(fixed.df$quant0.5[c(1, 3)]),
                   sum(fixed.df$quant0.5[c(5, 9)]),
                   sum(fixed.df$quant0.5[c(6, 11)])), digits=4)) %>%
  mutate(ID3_D = round(c(sum(fixed.df$quant0.5[c(1, 4)]),
                   sum(fixed.df$quant0.5[c(5, 10)]),
                   sum(fixed.df$quant0.5[c(6, 12)])), digits=4)) %>%
  mutate(ID1_P = round(c(sum(fixed.df$quant0.5[c(1, 2)]),
                   sum(fixed.df$quant0.5[c(5)]),
                   sum(fixed.df$quant0.5[c(6)])), digits=4)) %>%
  mutate(ID2_P = round(c(sum(fixed.df$quant0.5[c(1, 2, 3, 7)]),
                   sum(fixed.df$quant0.5[c(5, 9)]),
                   sum(fixed.df$quant0.5[c(6, 11)])), digits=4)) %>%
  mutate(ID3_P = round(c(sum(fixed.df$quant0.5[c(1, 2, 4, 8)]),
                   sum(fixed.df$quant0.5[c(5, 10)]),
                   sum(fixed.df$quant0.5[c(6, 12)])), digits=4)) %>%
  gather(Scenario, Median, -Parameter)

lb_fixedeffect.df <- data.frame(Parameter = c("Intercept","Scaled LAI", "Scaled Overall Seedling Cover")) %>%
  mutate(ID1_D = round(c(sum(fixed.df$quant0.025[c(1)]),
                   sum(fixed.df$quant0.025[c(5)]),
                   sum(fixed.df$quant0.025[c(6)])), digits=4)) %>%
  mutate(ID2_D = round(c(sum(fixed.df$quant0.025[c(1, 3)]),
                   sum(fixed.df$quant0.025[c(5, 9)]),
                   sum(fixed.df$quant0.025[c(6, 11)])), digits=4)) %>%
  mutate(ID3_D = round(c(sum(fixed.df$quant0.025[c(1, 4)]),
                   sum(fixed.df$quant0.025[c(5, 10)]),
                   sum(fixed.df$quant0.025[c(6, 12)])), digits=4)) %>%
  mutate(ID1_P = round(c(sum(fixed.df$quant0.025[c(1, 2)]),
                   sum(fixed.df$quant0.025[c(5)]),
                   sum(fixed.df$quant0.025[c(6)])), digits=4)) %>%
  mutate(ID2_P = round(c(sum(fixed.df$quant0.025[c(1, 2, 3, 7)]),
                   sum(fixed.df$quant0.025[c(5, 9)]),
                   sum(fixed.df$quant0.025[c(6, 11)])), digits=4)) %>%
  mutate(ID3_P = round(c(sum(fixed.df$quant0.025[c(1, 2, 4, 8)]),
                   sum(fixed.df$quant0.025[c(5, 10)]),
                   sum(fixed.df$quant0.025[c(6, 12)])), digits=4)) %>%
  gather(Scenario, LB, -Parameter)

ub_fixedeffect.df <- data.frame(Parameter = c("Intercept","Scaled LAI", "Scaled Overall Seedling Cover")) %>%
  mutate(ID1_D = round(c(sum(fixed.df$quant0.975[c(1)]),
                   sum(fixed.df$quant0.975[c(5)]),
                   sum(fixed.df$quant0.975[c(6)])), digits=4)) %>%
  mutate(ID2_D = round(c(sum(fixed.df$quant0.975[c(1, 3)]),
                   sum(fixed.df$quant0.975[c(5, 9)]),
                   sum(fixed.df$quant0.975[c(6, 11)])), digits=4)) %>%
  mutate(ID3_D = round(c(sum(fixed.df$quant0.975[c(1, 4)]),
                   sum(fixed.df$quant0.975[c(5, 10)]),
                   sum(fixed.df$quant0.975[c(6, 12)])), digits=4)) %>%
  mutate(ID1_P = round(c(sum(fixed.df$quant0.975[c(1, 2)]),
                   sum(fixed.df$quant0.975[c(5)]),
                   sum(fixed.df$quant0.975[c(6)])), digits=4)) %>%
  mutate(ID2_P = round(c(sum(fixed.df$quant0.975[c(1, 2, 3, 7)]),
                   sum(fixed.df$quant0.975[c(5, 9)]),
                   sum(fixed.df$quant0.975[c(6, 11)])), digits=4)) %>%
  mutate(ID3_P = round(c(sum(fixed.df$quant0.975[c(1, 2, 4, 8)]),
                   sum(fixed.df$quant0.975[c(5, 10)]),
                   sum(fixed.df$quant0.975[c(6, 12)])), digits=4)) %>%
  gather(Scenario, UB, -Parameter)


realeffect.df <- lb_fixedeffect.df %>%
  left_join(ub_fixedeffect.df,
            by = c("Parameter", "Scenario")) %>%
  left_join(mean_fixedeffect.df,
            by = c("Parameter", "Scenario"))%>%
  mutate(RR_lb = ifelse(exp(LB)>1, exp(LB)-1, exp(LB)-1), 
         RR_ub = ifelse(exp(UB)<1, exp(UB)-1, exp(UB)-1), 
         RR_med = ifelse(exp(Median)>1, exp(Median)-1, exp(Median)-1))
```

The figure below quantifies the uncertainty around the difference between species and their relationsihp with disturbance. The credible interval's of Dominant species 1 between disturbed and pristine areas of the rainforest do not overlap, so the data shows evidence of a definite difference. However, this demonstrates a large amount on uncertainty as the increase ranges from 1.4 to 66.3 of weighted SLA of species 1 in pristine rainforest areas. This difference between rainforest areas is not observed for the remaining species ID.

```{r}
# realeffect.df %>% filter(Parameter == "Intercept", Scenario == "ID1")

realeffect.df %>%
  filter(Parameter == "Intercept") %>%
  ggplot(aes(y = Scenario, x = exp(Median), xmin = exp(UB), xmax = exp(LB))) +
  geom_errorbarh() +
  theme_project() +
  ggtitle("Site and Dominant Species ID") +
  xlab("Real Intercept Effect - Credible Intervals") +
  ylab("Intercept Scenarios") +
  geom_vline(xintercept = 0) +
  scale_x_continuous(breaks = seq(0, 80, 5))


# ggsave(paste0(data_folder, "scale_sla_cw_", "intercept",".png"), width = 3.5, height = 2.5, dpi = 900)
```

In the figure below, the uncertainty around the LAI effect is demonstrated. As expected, the credible interval for species 1 does not include zero. This highlights that LAI has a positive affect on the weighted sla of species 1. For a unit increase in scaled LAI, the weighted SLA increases between 0.03 and 0.6. The data collected does not show a definitive relationship for species 2, however the distribution is more centered towards negative values, as suggested from the exploratory analysis. 

```{r}

realeffect.df %>%
  mutate(speciesid = paste0("Dom Species ",substr(Scenario, 3, 3))) %>%
  filter(Parameter == "Scaled LAI") %>%
  select(speciesid,RR_lb,  RR_med, RR_ub, Median, LB, UB, Parameter) %>%
  distinct() %>%
  ggplot(aes(y = speciesid, x = RR_med, xmin = RR_lb, xmax = RR_ub)) +
  geom_errorbarh() +
  theme_project() +
  ggtitle("Leaf Area Index") +
  xlab("Real LAI Effect - Credible Intervals") +
  ylab("Dominant Species ID") +
  geom_vline(xintercept = 0)


# ggsave(paste0(data_folder, "scale_sla_cw_", "lai",".png"), width = 3.5, height = 1.8, dpi = 900)
```

The last figure below demonstrates the relationship between overall seedling cover and different species' SLA. Overall, only species 1 responds positively to an increase in overall seedling cover, where as both species 2 and 3 do not have as definitive evidence.

```{r}
realeffect.df %>%
  mutate(speciesid = paste0("Dom Species ",substr(Scenario, 3, 3))) %>%
  filter(Parameter == "Scaled Overall Seedling Cover")  %>%
  select(speciesid,RR_lb,  RR_med, RR_ub, Median, LB, UB, Parameter) %>%
  distinct() %>%
  ggplot(aes(y = speciesid, x = RR_med, xmin = RR_lb, xmax = RR_ub))+
  geom_errorbarh() +
  theme_project() +
  ggtitle("Overall Seedling Cover") +
  xlab("Real Cover Effect - Credible Intervals") +
  ylab("Dominant Species ID") +
  geom_vline(xintercept = 0)
```


#### Variation Breakdown
In the figure below, we observe a different outcome than expected. Large variation was observed between quadrats for weighted SLA, however the INLA model shows that minimal variation was attributed to the random effects.

```{r}
## How to look at predictions and compare to original???
random <- summary(fit)$hyperpar
# random

randomeffects <- data.frame(hyperparameter = c("Residual", "Transect", "Quadrat:Transect"),
           precision = random[[1]],
           lb = random[[3]],
           ub = random[[5]]) %>%
  mutate(variance = 1/precision,
         varlb = 1/lb,
         varub = 1/ub) %>%
  mutate(totalvar = sum(variance),
         totallb = sum(varlb),
         totalub = sum(varub)) %>%
  mutate(explained = variance/totalvar,
         explainedlb = varlb/totallb,
         explainedub = varub/totalub) %>%
  arrange(desc(explained))

# 
randomeffects %>%
  ggplot(aes(y = hyperparameter, x = exp(variance), xmin = exp(varlb), xmax = exp(varub))) +
  geom_errorbarh() +
  theme_project() +
  ggtitle("Hyperparameters") +
  xlab("Credible Interval") +
  ylab("Hyperparameter")

randomeffects %>%
  mutate(`Variation Explained` = percent(explained)) %>%
  select(hyperparameter, `Variation Explained`)

# ggsave(paste0(data_folder, "scale_sla_cw_", "random",".png"), width = 3.5, height = 1.8, dpi = 900)
```


<!-- ##### Frequentist -->
<!-- ```{r} -->
<!-- lmer_formula <- log(sla_cw) ~  site + dom_species_id + site:dom_species_id + scaled_av_quad_lai +  scaled_av_quad_lai:dom_species_id + (1|site_trans/quadrat) -->

<!-- fit2 <- lmer(lmer_formula, -->
<!--              data = sla_ind.df) -->

<!-- summary(fit2) -->
<!-- ``` -->
