---
title: "model_development"
output: html_document
---

All predictor variables were first scaled so that for they would be comparable with eachother. Variables were then investigated separately against species richness to identify reasonable covariates for the model fit. 


```{r}
species_richness <- data.frame(species_richness_rq3.df) %>%
  rename(presence_richness = species_richness)
# str(species_richness)

#specify as factor
species_richness$site <- as.factor(species_richness$site)
species_richness$transect <- as.factor(species_richness$transect)
species_richness$quadrat <- as.factor(species_richness$quadrat)

#replace 0s
species_richness$dom_2_seedling_cover[species_richness$dom_2_seedling_cover==0] <- 0.000000000001

species_richness$dom_3_seedling_cover[species_richness$dom_3_seedling_cover==0] <- 0.000000000001



#scale variables

species_richness$dom_1_seedling_cover <- scale(species_richness$dom_1_seedling_cover)
species_richness$dom_2_seedling_cover <- scale(species_richness$dom_2_seedling_cover)
species_richness$dom_3_seedling_cover <- scale(species_richness$dom_3_seedling_cover)
species_richness$overall_seedling_cover <- scale(species_richness$overall_seedling_cover)
species_richness$dom_1_sla <- scale(species_richness$dom_1_sla)
species_richness$av_quad_compaction <- scale(species_richness$av_quad_compaction)
species_richness$av_trans_elevation <- scale(species_richness$av_trans_decomposition)
species_richness$min_temp <- scale(species_richness$min_temp)
species_richness$max_temp <- scale(species_richness$max_temp)
species_richness$dom_1_abundance<- scale(species_richness$dom_1_abundance)
species_richness$dom_2_abundance<- scale(species_richness$dom_2_abundance)
species_richness$dom_3_abundance<- scale(species_richness$dom_3_abundance)


#update dateframe (take out irrelevant variables)
species_richness <- subset(species_richness, select=-c(`dom_4_abundance`, `dom_4_seedling_cover`))
```

#### Site
Although there is differences in the range of species richness between the two disturbances, they exhibit very similar shapes in the above graph. Hence, the two categories may not be significantly different. However, for the sake of this project, the disturbance was investigated. 

```{r}
##species richness vs site
species_richness %>%
  ggplot(aes(x=site, y = presence_richness, col=site)) +
  geom_boxplot() +
  # geom_smooth(method="loess", span = 5) +
  scale_colour_manual(values = colours.site, name = "Site") +
  theme_project() +
  ggtitle("Species Richness vs Site")+
  xlab("Site") +
  ylab("Species Richness")

#species richness appear similar in both sites. However, the first and 3rd quantiles overlap and are very similar between both sites. There may not be a significant relation between the species richness and the disturbance. For the basis of our research, the variable SITE will still be included to verify its significance
```


#### Temperature
```{r}
##temperature range vs species richness
species_richness %>%
  ggplot(aes(x=max_temp, 
             y = presence_richness,
             col=site)) +
  geom_point()  +
  geom_smooth(method="lm",se=FALSE, span = 5) +
  theme_project() +
  scale_colour_manual(values = colours.site, name = "Site")+
  ggtitle("Species Richness vs Maximum Temperature")+
  xlab("Scaled Maximum Temperature") +
  ylab("Species Richness")
```

From the graph above, it appears that there is significant pattern exhibited between maximum temperature and species richness. Furthermore it does appear that the two disturbance categories intersect. However, upon investigation of model fit, interaction was not suited in the model. there seems to be a negative relationship between maximum temperature and species richness. 

#### Correlation
```{r}
#update species_richness
species_richness <- subset(species_richness, select = c(`site`, `quadrat`, `transect`,
                                        `dom_1_seedling_cover`,
                                         `dom_2_seedling_cover`,
                                        `dom_3_seedling_cover`,
                                        `overall_seedling_cover`,
                                         `dom_1_abundance`,
                                         `dom_2_abundance`,
                                         `dom_3_abundance`,
                                         `max_temp`, `dom_1_sla`, `dom_2_sla`, 
                                         `dom_3_sla`, `presence_richness`))


## TRANSFORM DATA:


SLA <- as.vector(t(species_richness[,-c(1,2,3,4,5,6,7,8,9,10,11,15)]))
abundance <- as.vector(t(species_richness[,-c(1,2,3,4,5,6,7,11,12,13,14,15)]))
quadrat <- rep(species_richness$quadrat, each=3)
species_ID <- rep(c(1,2,3), times=12) 
presence_richness <- rep(species_richness$presence_richness, each=3)
overall_seedling_cover <-rep(species_richness$overall_seedling_cover, each=3)
transect <- rep(species_richness$transect, each=3)
max_temp <- rep(species_richness$max_temp, each=3)
site <- rep(species_richness$site,each=3)


df1 <- data.frame (SLA=SLA, quadrat=quadrat, site=site, species_ID=species_ID,
                   presence_richness=presence_richness, transect=transect,
                   max_temp=max_temp,
                   overall_seedling_cover=overall_seedling_cover, abundance=abundance)
df1$species_ID <- as.factor(df1$species_ID)
df1 <- mutate(df1, site_trans = factor(paste0(df1$site,df1$transect)))


df2<- na.omit(df1)

correlation_analyse <- subset(df2, select=-c(`species_ID`, `transect`, `quadrat`, `site`, `site_trans`))

cor(correlation_analyse %>% select(-presence_richness), use = "complete.obs") %>%
  round(digits = 2)

```

The correlation matrix indicates that none of the predictor variables are correlated with eachother. This implies that there is no violation in assumption for performing ther regression. 